
---
title: "Dispersal Model Graphs"
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r docSettings, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE)

library(ggplot2)
library(plyr)


folder <- "G:/ownCloud/DisperalSimulationOutput/"

dis_aves <- read.csv(paste(folder, "DispersalSummary27Sept_DataJulyCombine.csv", sep = ""))


mytheme <- theme_bw(base_size=25)  + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.margin= unit(0.75, "lines"),
		plot.margin=unit(c(3,1,1.5,1.2),"cm"), panel.border = element_rect(fill = NA, colour = "black", linetype=1, size = 1), legend.position="bottom", 
		legend.background = element_rect(fill="white", size=0.5, linetype="solid", colour ="black"), legend.text=element_text(size=15))


# constant variables

env <- 0.0
no_off <- 6 


dis_sub <- subset(dis_ply, input_var == env & max_no_off == no_off)

```



Metapopulation Age Until Extinction
=====

```{r metapop, fig.height=12, fig.width=14}



ggplot(dis_sub, aes(x = Comp_meas, y = log10(PopAge.Mean), colour = as.factor(ad_dsp_fd))) + 
		geom_point(size = 5, position = position_jitter(w = 0, h = 0.05)) + 
		geom_line(size = 2, position = position_jitter(w = 0, h = 0.01)) + mytheme + ylab("Log max metapopulation age") + 
		scale_colour_discrete("Size needed to disperse") + xlab("Competition measure") +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 3.0))


```

(@) _Figure :Metapopulation survival against competition type, where competition
type ranges from 0 to 1, with 0 being full scramble competition and 1 is full
contest competition. Environmental variance is `r env` and number of offspring
set to `r no_off'. No generations removed_



Population survival
=====

```{r popSurv, fig.height=12, fig.width=14}

ggplot(dis_sub, aes(x = Comp_meas, y = log10(survival_all.mean), colour = as.factor(ad_dsp_fd))) + 
		geom_point(size = 5, position = position_jitter(w = 0, h = 0.05)) + 
		geom_line(size = 2, position = position_jitter(w = 0, h = 0.01)) + 
		mytheme + ylab("Log average population survival") + 
		scale_colour_discrete("Size needed to disperse") + xlab("Competition measure") +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 3.0))


```

(@) _Figure :Population survival against competition type, where competition
type ranges from 0 to 1, with 0 being full scramble competition and 1 is full
contest competition. Environmental variance is `r env` and number of offspring
set to `r no_off'. All generations included. Survival calculated from survival
function_

