
---
title: "Dispersal Model Graphs"
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    reference_docx: FormatReferenceDoc.docx

---

```{r docSettings, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, fig.height=4, fig.width=5)

mytheme <- theme_bw(base_size=10)  + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    	panel.border = element_rect(fill = NA, colour = "black", linetype=1, size = 0.5), legend.position="bottom", 
		legend.background = element_rect(fill="white", size=0.7, linetype="solid", colour ="black"), legend.text=element_text(size=6))

pointSize <- 2
lineSize <-0.5


# constant variables
env1<- 0.0
no_off <- 6 

subDispFile <- subset(importDispFile, Comp_meas != 0.5)
subDispFile <- subset(subDispFile, max_no_off == no_off & input_var == env1)
nrow(subDispFile)

xtabs(~ Comp_slope + ad_dsp_fd + input_var,  data = subDispFile)


```



### Metapopulation Age Until Extinction



```{r metapop, , results = 'asis'}


ggplot(subDispFile, aes(x = Comp_meas, y = log10(metPopAgeMax), colour = as.factor(ad_dsp_fd))) + 
		geom_point(size = pointSize, position = position_jitter(w = 0, h = 0.05)) + 
		geom_line(size = lineSize, position = position_jitter(w = 0, h = 0.01)) + mytheme + ylab("Log max metapopulation age") + 
		scale_colour_discrete("Size needed to disperse") + xlab("Competition measure") +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 3.0))


```

(@) _Figure :Metapopulation survival against competition type, where competition
type ranges from 0 to 1, with 0 being full scramble competition and 1 is full
contest competition. Environmental variance is `r env1` and number of offspring
set to `r no_off`. No generations removed_


As competition changes from scramble to contest competition the metapopulation
age increases, but this interacts with the body size needed to disperse, unless
the populations survive to 500 generations, in which cases obviously.

**Both dipsersal and intraspecific compeition type affects metapopulation survival**


#### Why dispersal increases metapopulation survival?

The simulation only starts with x number of colonies, but there are ‘spaces’ for
200. More dispersal means that these spaces get filled up. 

#### How does this interact with competition? 

If food is shared via contest competition then normally some individuals will
get enough food to disperse, even if individuals have to be large to disperse. 
However if food is shared via contest competition then this is not the case.


Population survival
---

```{r popSurv}

ggplot(subDispFile, aes(x = Comp_meas, y = log10(survivalMean_all), colour = as.factor(ad_dsp_fd))) + 
		geom_point(size = pointSize, position = position_jitter(w = 0, h = 0.05)) + 
		geom_line(size = lineSize, position = position_jitter(w = 0, h = 0.01)) + 
		mytheme + ylab("Log average population survival") + 
		scale_colour_discrete("Size needed to disperse") + xlab("Competition measure") +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 3.0)) 


```

(@) _Figure :Population survival against competition type, where competition
type ranges from 0 to 1, with 0 being full scramble competition and 1 is full
contest competition. Environmental variance is `r env1` and number of offspring
set to `r no_off`. All generations included. Survival calculated from survival
function_

As competition increases the population survival time increases. But the size
needed to disperse surprisingly does not have a massive effect on population
survival esp compared to competition.

**The main thing that affects population survival is compeition type, dispersal has little effect**


Metapopulation survival against population survival
---


```{r MetSurvpopSurv}

ggplot(subDispFile, aes(x = log10(survivalMean_all), y = log10(metPopAgeMax), colour = as.factor(ad_dsp_fd))) +
		mytheme + 
		geom_smooth(se = FALSE, size = 1, lty = 3) +
		geom_point(size = pointSize, position = position_jitter(w = 0, h = 0.05)) + 
		ylab("Log metapopulation survival") + 
		xlab("Log population survival") +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 3.0)) +
		scale_x_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 3.0)) + 
		scale_colour_discrete("Size needed to disperse")


```

(@) _Figure :Metapopulation against population survival. Environmental variance
is `r env1` and number of offspring set to `r no_off`. All generations included.
Survival calculated from survival function_

From this graph we can see that dispersal affects whether populations survival
affects metapopulation survival. When the size needed to disperse is 0.2 (i.e.
low) then the metapopulation survives to 500 generations regardless of the
survival of the populations. The higher the disperal size is, the more the
population survival affects the metapopulation survival.


Metapopulation survival and dispersal
---


```{r MetSurvTotNumDispersers}
	
ggplot(subDispFile, aes(x = any_disp, y = log10(metPopAgeMax), colour = as.factor(Comp_meas))) +
		mytheme + geom_boxplot() + ylab("Log metapopulation survival") + 
		xlab("") + scale_colour_discrete("Competition")

```

(@) _Figure : Comparing metapopulation survival to whether any populations produced dispersers_ 

This shows how metapopulations have short survival if dispersal is restricted, but that metapopulations can survive no dispersal if competition within populations is contest like.





What affects dispersal?
---
### make summary file for this graph

```{r WhatAfftsDispersal}

ave_subDispFile<- ddply(subDispFile, .(Comp_meas, ad_dsp_fd), summarise,
		N_all = length(!is.na(fileNum)),
		meanDispBin = mean(any_disp, na.rm = FALSE))

ggplot(ave_subDispFile, aes(x = as.factor(Comp_meas), y = as.factor(ad_dsp_fd), fill = meanDispBin))  + geom_tile() +
		mytheme + ylab("Adult dispersal size") +  xlab("Competition") + scale_colour_continuous("Dispersal binary by metapopulation")

```

(@) _Figure : Comparing metapopulation survival to whether any populations produced dispersers_ 

This shows how metapopulations have short survival if dispersal is restricted, but that metapopulations can survive no dispersal if competition within populations is contest like.



Conclusion
---
Competition affects population survival and therefore metapopulation survival,
but low population survival is off-set by disperal to increase metapopulation
survival.


Metapopulation and population survival and environmental variance
===


```{r envFile, include = FALSE}

set_ad_dsp_fd1 <- 0.8
set_ad_dsp_fd2 <- 0.6

subDispFile <- subset(importDispFile, max_no_off == no_off)

subDispFile <- subset(subDispFile, Comp_meas != 0.5)

#disaves_subVar <-  subset(dis_aves, max_no_off == no_off)
#disaves_subVar <- subset(disaves_subVar, ad_dsp_fd == set_ad_dsp_fd1 | ad_dsp_fd == set_ad_dsp_fd2)


```

###TODO: could remove come layers of comp variables

Metapopulation Survival
---
```{r metapopVar}

ggplot(importDispFile, aes(x = input_var, y = log10(metPopAgeMax), colour = as.factor(Comp_meas))) + 
		geom_point(size = pointSize, position = position_jitter(w = 0, h = 0.05)) + 
		geom_line(size = lineSize, position = position_jitter(w = 0, h = 0.01)) + mytheme + ylab("Log max metapopulation age") + 
		scale_colour_discrete("Competition") + xlab("Environmental variation") +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 3.0)) + facet_wrap(~ad_dsp_fd)
```

(@) _Figure :Metapopulation survival environmental variance. Number of offspring
set to `r no_off`. All generations included_

Intermediate environmental variance increases metapopulation survival for some
competition measures when dispersal is restricted.


Population Survival vs Metapopulation survival
---

```{r MetSurvVsPopSurv, fig.height=8, fig.width=10}

ggplot(importDispFile, aes(x = log10(survivalMean_all), y = log10(metPopAgeMax), colour = as.factor(input_var))) + 
		geom_point(size = pointSize, position = position_jitter(w = 0, h = 0.05)) + 
		mytheme + ylab("Log max metapopulation age") + 
		geom_line(size = lineSize, position = position_jitter(w = 0, h = 0.01)) +
		scale_colour_discrete("Variance") + xlab("Population Survival") +
		facet_grid(ad_dsp_fd ~ Comp_meas)
```






