
---
title: "Dispersal Model Graphs"
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    reference_docx: FormatReferenceDoc.docx
    fig_caption: true

---

```{r docSettings, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, fig.height=3, fig.width=6, dpi=400)

mytheme <- theme_bw(base_size=10)  + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    	panel.border = element_rect(fill = NA, colour = "black", linetype=1, size = 0.5), 
		legend.background = element_rect(fill="white", size=0.5, linetype="solid", colour ="black"), legend.text=element_text(size=8), 
		strip.background = element_rect(fill="white", size=0.7, linetype="solid", colour ="black"))

pointSize <- 1
lineSize <-0.5


# constant variables
env1<- 0.0
no_off <- 6 

subDispFile <- subset(importDispFile, Comp_meas != 0.5)

subDispFile <- subset(subDispFile, max_no_off == no_off & input_var == env1)
nrow(subDispFile)

xtabs(~ Comp_slope + ad_dsp_fd + input_var,  data = subDispFile)


```

# No environmental variation

## Metapopulation survival


```{r metSurv, , results = 'asis', fig.cap = "This is a figure caption for the metsurv figure"}

aveFile <- ddply(subDispFile, .(ad_dsp_fd, Comp_meas), summarize, 
		metPopAgeMax = mean(metPopAgeMax))

png(filename = "MetSurv.png", width = 1000, height = 650, units = "px", res = 200, pointsize = 10)

ggplot(aveFile, aes(x = Comp_meas, y = log10(metPopAgeMax))) + 
		geom_point(size = pointSize, position = position_dodge(width = 0.02), aes(shape = as.factor(ad_dsp_fd))) + 
		geom_line(size = lineSize, aes(linetype = as.factor(ad_dsp_fd))) + mytheme + ylab("metapopulation survival ") + 
		scale_shape_discrete("dispersal\nminimum\nsize") + scale_linetype_discrete("dispersal\nminimum\nsize") + 
		xlab("competition measure") +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 3.0))
 
dev.off()

```

(@) _Figure [MetSurv]:Metapopulation survival against competition type by
minimum dispersal size. Competition type ranges from 0 to 1, with 0 being
full scramble competition and 1 is full contest competition. Individual size
varies from 0 to 1. Environmental variance is `r env1`._


Metapopulation survival against population survival
---


```{r MetSurvPop, fig.height=4, fig.width=9}

appender <- function(string, myText = "dispersal size:") paste0(myText, string)

png(filename = "MetSurvPop.png", width = 1300, height = 750, units = "px", res = 200, pointsize = 10)


ggplot(subDispFile, aes(x = log10(survivalMean_all), y = log10(metPopAgeMax))) +
		mytheme + 
		geom_point(size = 2, color = "black", position = position_jitter(w = 0.05, h = 0.1), 
				aes(shape = as.factor(Comp_meas))) + 
		ylab("metapopulation survival") + 
		xlab("population survival") +
		geom_smooth(se = FALSE, method = "lm", formula = y ~ x + I(x^2),  color = "black", size = 0.4) +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 2.7)) +
		scale_x_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 2.7)) + 
		scale_shape_manual("competition\nmeasure", values=c(0, 1, 2, 3, 18, 20)) + 
		facet_grid(~ad_dsp_fd, scales = "fixed", labeller = as_labeller(appender)) +
		theme(legend.position="bottom")
 dev.off()

```

(@) _Figure [MetSurvPop]: Population survival against metapopulation survival,
by minimum adult dispersal size and competition type. Competition type ranges
from 0 to 1, with 0 being full scramble competition and 1 is full contest
competition. There is no environmental variation._



Metapopulation survival and dispersal
---


```{r MetDis}
	
aveFile <- ddply(subDispFile, .(ad_dsp_fd, Comp_meas), summarize, 
		any_disp = mean(any_disp),
		metPopAgeMax = mean(metPopAgeMax))

png(filename = "MetDis.png", width = 900, height = 550, units = "px", res = 200, pointsize = 10)

ggplot(aveFile, aes(x = any_disp, y = log10(metPopAgeMax))) + 
		stat_smooth(method = "lm",  formula  = y~ x + I(x^2),se = FALSE, color = "black", size = 0.5) + 
		mytheme + 
		geom_point(size = pointSize, position = position_jitter(w = 0.07, h = 0.02),  aes(shape = as.factor(ad_dsp_fd))) + 
		ylab("metapopulation survival ") + 
		xlab("dispersal within metapopulation") + scale_shape_discrete("dispersal\nminimum\nsize") + 
		scale_x_continuous(breaks=c(0, 1), limits = c(-0.2, 1.2), labels = c("no", "yes"))

dev.off()

```
 
(@) _Figure [MetDis]: Comparing metapopulation survival to a binary measure of
whether any populations within the metapopulation produced dispersers at any
time. 0 means no disperal took place, 1 dispersal did take place. No
environmental variation_





What affects dispersal?
---

```{r Disp, fig.height=3, fig.width=4}

ave_subDispFile<- ddply(subDispFile, .(Comp_meas, ad_dsp_fd), summarise,
		N_all = length(!is.na(fileNum)),
		meanDispBin = mean(any_disp, na.rm = FALSE))

png(filename = "Disp.png", width = 800, height = 700, units = "px", res = 200, pointsize = 10)

ggplot(ave_subDispFile, aes(x = as.factor(Comp_meas), y = as.factor(ad_dsp_fd), fill = meanDispBin))  + 
		geom_tile(colour = "white", size=0.1) +
		mytheme + ylab("dispersal minimum size") +  xlab("competition measure") + 
		scale_fill_gradient(low="black", high="grey80", guide = FALSE) +
		geom_rect(data = ave_subDispFile, aes(xmin=2.525, xmax=3.475, ymin=2.52, ymax=3.48), fill='grey25', 
				colour = 'black', alpha=0.01, size = 1, lty = 2)

dev.off()

```

(@) _Figure [Disp]: Showing how competition type and minimum adult dispersal
size interact to affect whether any dispersal took place. Black squares
indicate no dispersal took place, light grey squares indicate dispersal occurred.
The square with the black outline is the one combination of competition and
minimum dispersal size where dispersal did take place, but the metapopulation
did not survive to 500 generations.n Environmental variation is set to zero._



# With environmental variance

```{r EnvMetPop, include = FALSE}

set_ad_dsp_fd1 <- 0.8
set_ad_dsp_fd2 <- 0.6

subDispFile <- subset(importDispFile, max_no_off == no_off)

subDispFile <- subset(subDispFile, Comp_meas != 0.5 & input_var != 0.05 & input_var != 0.15)

nrow(subDispFile)

#disaves_subVar <-  subset(dis_aves, max_no_off == no_off)
#disaves_subVar <- subset(disaves_subVar, ad_dsp_fd == set_ad_dsp_fd1 | ad_dsp_fd == set_ad_dsp_fd2)

xtabs(~ Comp_slope + ad_dsp_fd + input_var,  data = subDispFile)

```

## Metapopulation Survival

```{r EnvMetSurv, fig.height=4}
#geom_smooth(se = FALSE, method = "lm", formula = y ~ x + I(x^2))

subSubFile <- subset(subDispFile, ad_dsp_fd == 0.6 | ad_dsp_fd == 0.8 | ad_dsp_fd == 1.2)

appender <- function(string, myText = "dispersal size:") paste0(myText, string)

png(filename = "EnvMetSurv.png", width = 1100, height = 750, units = "px", res = 200, pointsize = 10)
#formula = y ~ x + I(x^2)+ exp(-x)

# how to use nls to fit formual
# https://github.com/tidyverse/ggplot2/issues/1510

ggplot(subSubFile, aes(x = input_var, y = log10(metPopAgeMax))) + 
		geom_point(size = pointSize, position = position_jitter(w = 0, h = 0), aes(shape = as.factor(Comp_meas))) + 
		geom_smooth(se = FALSE, method = "lm",  formula = y ~ x + I(x^2), color = "black", size = 0.4, aes(linetype = as.factor(Comp_meas))) + 
		mytheme + ylab("metapopulation survival ") + 
		scale_linetype_discrete("competition\nmeasure") + 
		scale_shape_discrete("competition\nmeasure") + 
		xlab("environmental variation")+ facet_grid(ad_dsp_fd~., labeller = as_labeller(appender)) + 
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 2.9))
		

dev.off()

```

(@) _Figure [EnvMetSurv]:Comparing environmental variation to maximum
metapopulation age by competition type, looking only at minimum adult disperal
size 0.6 and 0.8_


## Population Survival

```{r EnvPopSurv, fig.height=4}


png(filename = "EnvPopSurv.png", width = 1100, height = 750, units = "px", res = 200, pointsize = 10)

ggplot(subSubFile , aes(x = input_var, y = log10(survivalMean_all))) + 
		geom_point(size = pointSize, position = position_jitter(w = 0, h = 0), aes(shape = as.factor(Comp_meas))) + 
		geom_smooth(se = FALSE, method = "lm", formula = y ~ x + I(x^2), color = "black", size = 0.4, aes(linetype = as.factor(Comp_meas))) + 
		mytheme + ylab("population survival ") + 
		scale_linetype_discrete("competition\nmeasure") + 
		scale_shape_discrete("competition\nmeasure") + 
		xlab("environmental variation") +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 2.9)) + 
		facet_grid(ad_dsp_fd~., labeller = as_labeller(appender))

dev.off()

```

(@) _Figure [EnvPopSurv]:Population survival against environmental variance by
competition type, looking only at minimum adult dispersal size 0.6 and 0.8._


What restricts dispersal?
---

```{r EnvDisp, fig.height=3, fig.width=4}


ave_subDispFile<- ddply(subDispFile, .(Comp_meas, ad_dsp_fd), summarise,
		N_all = length(!is.na(fileNum)),
		meanDispBin = mean(any_disp, na.rm = FALSE))

png(filename = "EnvDisp.png", width = 800, height = 700, units = "px", res = 200, pointsize = 10)

ggplot(ave_subDispFile, aes(x = as.factor(Comp_meas), y = as.factor(ad_dsp_fd), fill = meanDispBin))  + geom_tile(colour = "white", size=0.1) +
		mytheme + ylab("minimum dispersal size") +  xlab("competition measure") + 
		scale_fill_gradient(low="black", high="grey80", guide = FALSE) 
		#facet_wrap(~input_var)

dev.off()

```

(@) _Figure [EnvDisp]: Showing how competition type and minimum adult dispersal
size interact to affect whether any dispersal took place with environmental
variation. Black squares indicate no dispersal took place, light grey squares
indicate dispersal occurred and intermediate greys indicate dispersal took place
in some metapopulation.  With environmental variation dispersal has gone from
zero to some dispersal when size is 0.6 and competition is 0, size is 0.8, comp
is zero, and when size is 0.8 and comp is 0.2_


Dispersal amount and environmental variation
---

```{r EnvVarDisp, fig.height=3, fig.width=6}

dispEnv <- subset(subDispFile, (ad_dsp_fd == 0.6 & Comp_meas == 0) | (ad_dsp_fd == 0.8 & Comp_meas == 0) | (ad_dsp_fd == 0.8 & Comp_meas == 0.2))

dispEnv$all_ave_num_disp <- ifelse(is.na(dispEnv$all_ave_num_disp) == TRUE , 0, dispEnv$all_ave_num_disp)

dispEnv$Legend <- ifelse(dispEnv$ad_dsp_fd == 0.6 & dispEnv$Comp_meas == 0, "comp=0.0 and dispersal size=0.6", 
		ifelse(dispEnv$ad_dsp_fd == 0.8 & dispEnv$Comp_meas == 0, "comp=0.0 and dispersal size=0.8", 
				ifelse(dispEnv$ad_dsp_fd == 0.8 & dispEnv$Comp_meas == 0.2, "comp=0.2 and dispersal size=0.8", "MISTAKE")))

dispSum <- summarySE(dispEnv, measurevar="all_ave_num_disp", groupvars=c("input_var","Legend"))

png(filename = "EnvVarDisp.png", width = 1300, height = 700, units = "px", res = 200)

ggplot(dispSum, aes(x=input_var, y=all_ave_num_disp)) + 
    geom_errorbar(aes(ymin=all_ave_num_disp-se, ymax=all_ave_num_disp+se), width=.03) +
    geom_point(size = 2, aes(shape = Legend)) + mytheme+
	geom_line(aes(linetype = Legend)) + theme(legend.title=element_blank()) + 
    xlab("environmental variation") + ylab("mean count of dispersers per generation") +
	scale_shape_manual(values=c(0, 2, 19)) +
	scale_linetype_manual(values=c(6, 2, 1))

dev.off()
    
 ```

(@) _Figure [EnvVarDisp]: Average of log10 number of dispersing colonies per
time step against environmental variation._ 


# Graphs removed?

## Metapopulation vs population survival by minimum disperal size



```{r EnvMetSurvPop}



ggplot(subDispFile, aes(x = log10(survivalMean_all), y = log10(metPopAgeMax))) + 
		geom_point(size = pointSize, position = position_jitter(w = 0, h = 0.05), aes(shape = as.factor(ad_dsp_fd))) + 
		mytheme + ylab("Log max metapopulation age") + 
		geom_smooth(se= FALSE, color = "black", aes(linetype = as.factor(ad_dsp_fd)), size = 0.4) +
		scale_linetype_discrete("Adult Dispersal Limit") + 
		scale_shape_discrete("Adult Dispersal Limit") +
		xlab("Population Survival") +
		scale_y_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 2.7)) +
		scale_x_continuous(breaks=seq(0, 3.0, by=0.5), limits = c(0, 2.7))


```

(@) _Figure [EnvMetSurvPop]_

## Metapopulation survival and dispersal

```{r EnvMetDisp, fig.height=3.5, fig.width=10}

appender <- function(string, myText = "Competition:") paste0(myText, string)


ggplot(subDispFile, aes(x = any_disp, y = log10(metPopAgeMax))) + 
		stat_smooth(se = FALSE, color = "black", size = 0.4, method = "lm", formula = y ~ x + I(x^2)+ exp(-x)) + 
		mytheme + 
		geom_point(size = pointSize, position = position_jitter(w = 0.07, h = 0.02),  aes(shape = as.factor(ad_dsp_fd))) + 
		ylab("Log metapopulation survival") + 
		xlab("Did any dispersal take place?") + scale_shape_discrete("Dispersal\nMin Size") + 
		scale_x_continuous(breaks=seq(0, 1.0, by=1), limits = c(-0.2, 1.2)) +
		facet_grid(~Comp_meas, labeller = as_labeller(appender)) +
		theme(legend.position="bottom")

```

(@) _Figure [EnvMetDisp]_

 