
---
title: "Weight Vs Colony Size Results with instar as numeric"
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r docSettings, include = FALSE}
## Make sure to run R code /CurrentPaperCode_9Aug/_RUNFIRST
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, warning = FALSE)
modelList <-  list(test = c(), fullModel = c())
no_nest <- nlevels(spidersMul$NestID)

table(spiders$Instar)
	
```

Remember Note: If line on graph is blue R could not plot the lmer, plotting a
simple lm instead[1] 

### Leg length against colony size


```{r LegInstarNumber, results='asis',  echo = FALSE}
##### Leg length vs instar

FullModelLeg <- lmer(logLeg ~ logCtFm + InstarNumber + logCtFm:InstarNumber + logCtFm:InstarNumber:InstarSex +  
    			(1 | NestID), data = spidersMul, REML = FALSE)
modelList$test <- c(modelList$test, "Leg length vs. colony size")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModelLeg))

#testing against instar
InstarModel <- update(FullModelLeg , .~. - InstarNumber -logCtFm:InstarNumber - logCtFm:InstarNumber:InstarSex)
InstarResults <- outputResultsWord(FullModelLeg, InstarModel)
	
```

The model with the lowest AIC value included the two-way interaction 
colony size by instar age and the 
three-way interaction colony size by instar age by instar sex as fixed effects,
but did not include the instar age by instar sex interaction
`r figNumLookup$InstarLeg[1]`. After confirming, not surprisingly, that
leg length was highly correlated with instar age (lmer;
$\chi$^2^~`r InstarResults[[1]]` ,`r InstarResults[[2]]`~=
`r InstarResults[[3]]`, p = `r InstarResults[[4]]` `r InstarResults[[5]]`), we
found that

```{r LegVsNestSize, results='asis',  echo = FALSE}
##### Leg length vs nest size
NSModel <- update(FullModelLeg , .~. - logCtFm -logCtFm:InstarNumber - logCtFm:InstarNumber:InstarSex)
NSResults <- outputResultsWord(FullModelLeg , NSModel)	
```

leg length increased as colony size increased 
(lmer; $\chi$^2^~`r NSResults[[1]]`
,`r NSResults[[2]]`~= `r NSResults[[3]]`, p = `r NSResults[[4]]`
`r NSResults[[5]]`, `r figNumLookup$Fig_LegLengthVsColonySize[1]`, 

```{r LeglogCtFmByInstarNumber, results='asis',  echo = FALSE}
##### Leg length vs logCtFm by InstarNumber interaction
Instar2IntModel <- update(FullModelLeg , .~. - logCtFm:InstarNumber - logCtFm:InstarNumber:InstarSex)
Instar2IntResults <- outputResultsWord(FullModelLeg , Instar2IntModel)	
```

but with a significant interaction with instar
age (lmer; $\chi$^2^~`r Instar2IntResults[[1]]` ,`r Instar2IntResults[[2]]`~=
`r Instar2IntResults[[3]]`, p = `r Instar2IntResults[[4]]`
`r Instar2IntResults[[5]]`)

```{r Leg3Interaction, results='asis',  echo = FALSE}
##### Leg length vs three way interaction
Instar3IntModel <- update(FullModelLeg , .~. - logCtFm:InstarNumber:InstarSex)
Instar3IntResults <- outputResultsWord(FullModelLeg , Instar3IntModel)	
```

and a significant three-way interaction between colony size, instar age and
instar sex (lmer; $\chi$^2^~`r Instar3IntResults[[1]]`
,`r Instar3IntResults[[2]]`~= `r Instar3IntResults[[3]]`, p =
`r Instar3IntResults[[4]]` `r Instar3IntResults[[5]]`). 


```{r LegIndInstar, results='asis',  echo = FALSE}
##### Leg length vs nest size for each instar
FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
AdultRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Sub2"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Sub2"))
Sub2Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Sub1"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Sub1"))
Sub1Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Juv4"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Juv4"))
Juv4Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))
AdMaleRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))
SubMaleRes <- outputResultsWord(FullModel, RedModel)	
```

Due to this significant interaction we performed tests on each instar
individually. We found that leg length increased with colony size in the older
instars, but not significantly so in the younger ones
`r figNumLookup$Table_InstarLeg[1]` and   
`r figNumLookup$Fig_LegLengthVsColonySize[1]`.




| Instar and sex   | Instar Age    | $\chi$^2^ |  p value| 
|----------|----|---------------------|--------------------------------------| 
|Juv4 |4| `r (Juv4Res[[3]])` |   `r Juv4Res[[4]]` `r Juv4Res[[5]]`  | 
| Sub1 Female|5| `r (Sub1Res[[3]])` |   `r Sub1Res[[4]]` `r Sub1Res[[5]]`  | 
| Sub2 Female|6| `r (Sub2Res[[3]])` |   `r Sub2Res[[4]]` `r Sub2Res[[5]]`  | 
|Adult Female |7|  `r (AdultRes[[3]])` |`r AdultRes[[4]]` `r AdultRes[[5]]`  |  
|Sub Male|5| `r (SubMaleRes[[3]])` |`r SubMaleRes[[4]]` `r SubMaleRes[[5]]`|
|Adult Male |6| `r (AdMaleRes[[3]])` |`r AdMaleRes[[4]]` `r AdMaleRes[[5]]` | 


`r figNumLookup$Table_InstarLeg[1]`

_TABLE: Results of separate analysis of leg length against colony size for
each instar and the two sexes. Leg length increases with colony size in the
overall model (p = `r NSResults[[4]]` `r NSResults[[5]]` ). When tested
individually the relationship is only significant for the older instars._


```{r LegInstarGridGraph, fig.height=9, fig.width=14}
InstarGridGraph(spidersMul, "logLeg", "Leg Length - log transformed", "n", "", FullModelLeg)

figNumLookup$Fig_LegLengthVsColonySize

```
  
_FIGURE:  Leg length (tiba plus patella) as a function of colony size
with the full linear model, which contains a significant interaction
with colony size, superimposed. Overall, leg length increased with colony size
(p = `r NSResults[[4]]` `r NSResults[[5]]`), but with a significant
interaction between colony size and instar,. When tested
individually, only the older instars exhibited a significant relationship. 
n= `r no_nest` colonies._


### Individual condition against colony size


```{r CondNS, results='asis',  echo = FALSE}
##### conditionh vs colony size
FullModel <- lmer(condResiduals ~  logCtFm + logCtFm:InstarNumber  +  (1|NestID), data = spidersMul, REML = FALSE)
modelList$test <- c(modelList$test, "Condition vs. colony size")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModel))

NSModel <- update(FullModel, ~ . - logCtFm - logCtFm:InstarNumber)
NSResults <- outputResultsWord(FullModel, NSModel)

```
The
model with the lowest AIC value included only one interaction term, instar age by colony size, and 
did not include instar sex or instar age as fixed effects `r figNumLookup$Table_models` . 
The effect of colony size was significant (lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~ =
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`) 
with individual condition decreasing as colony size increased `r figNumLookup$Fig_ConditionVsColSize`.

```{r ConditionInteraction, results='asis',  echo = FALSE}
# condition vs logCtFm by instar number interaction
IntModel <- update(FullModel, . ~ . - logCtFm:InstarNumber)
IntResults <- outputResultsWord(FullModel, IntModel)		
```

There was a significant interaction between instar age
 and colony size (lmer; $\chi$^2^~`r IntResults[[1]]`, `r IntResults[[2]]`~ =
`r IntResults[[3]]`, p = `r IntResults[[4]]` `r IntResults[[5]]`), with condition appearing to decrease at a faster rate 
with colony size as the instar age 
increases.

```{r ConditionAdultOnly, results='asis',  echo = FALSE}
# Only adult significant post-hoc
FullModelAdOnly <- lmer(condResiduals ~  logCtFm +  (1|NestID), data = subset(spidersMul, Instar == "Adult"), REML = FALSE)
RedModAd <- update(FullModelAdOnly, .~. - logCtFm)
AdultResults <- outputResultsWord(FullModelAdOnly, RedModAd)
```

When performing tests on the instars individually, only adult female condition
decreased significantly with colony size (lmer; $\chi$^2^~`r AdultResults[[1]]`,
`r AdultResults[[2]]`~ = `r AdultResults[[3]]`, p = `r AdultResults[[4]]`
`r AdultResults[[5]]`).

```{r ConditionInstarGridGraph, fig.height=9, fig.width=14}
InstarGridGraph(spidersMul, "condResiduals", "Individual Condition", "n", "", FullModel, "y")

figNumLookup$Fig_ConditionVsColSize

```
  
_FIGURE : Individual condition against colony size, with the linear model
superimposed. Overall condition decreases with colony size (p =
`r NSResults[[4]]` `r NSResults[[5]]`), with  a significant interaction with
instar age (p = `r InstarResults[[4]]` `r InstarResults[[5]]`), but not
instar sex. Gradient increases from juv4 to adult. _




### Within-colony variance against colony size

#### Leg length


```{r LegVariacne, echo = FALSE}

meanLegBootVar <- round(mean(legBootVar$bootSD_var),2)
SELegBootVar  <- round(sd(legBootVar$bootSD_var)/sqrt(length(legBootVar$bootSD_var)), 2)

```
There was no significant effect of nest size on within-colony variance in leg length. However, before transformation, the average leg variance was
`r meanLegBootVar` $\pm$ `r SELegBootVar`, which is small given that the range of possible values is between zero and one.

#### Variance

```{r CondVariance, results='asis',  echo = FALSE, message = FALSE, warning = FALSE}
# mean and SD
meanCondBootVar <- round(mean(condBootVar$bootSD_var), 2)
SECondBootVar  <- round(sd(condBootVar$bootSD_var)/sqrt(length(legBootVar$bootSD_var)),2)

# formatting the data
totSpis<- sum(condBootVar$N)
condBootVar$lmrWgts <- condBootVar$N/totSpis
condBootVar$bootVarTrans <- asin(sqrt(condBootVar$bootSD_var))
condBootVar$bootVarTrans <- condBootVar$bootVarTrans*100 # Making variance a percentage
condBootVar$bootVarTrans <- condBootVar$bootVarTrans +1 # have to add a small amount or glmer "can't find starting values"

# running the model
condBootFormula <-  bootVarTrans ~ logCtFm + InstarNumber:InstarSex + InstarSex:I(InstarNumber^2)
varBootCondMod <- glmmPQL(condBootFormula, ~1|NestID, family = gaussian(link = "log"), data = condBootVar, weights = lmrWgts, niter = 10)		
varBootCondAnova <- addStarsOnly_anova(varBootCondMod)
modelList$test <- c(modelList$test, "Condition Variance vs. colony size")
modelList$fullModel <- c(modelList$fullModel, docxFmula(condBootFormula))

# seperating the results for easier printing below
NSCondRes <- varBootCondAnova[which(varBootCondAnova$parameters == "logCtFm"),]
InstarSexCondRes <- varBootCondAnova[which(varBootCondAnova$parameters == "InstarNumber:InstarSex"),]
InstarSexSqrCondRes <- varBootCondAnova[which(varBootCondAnova$parameters == "InstarSex:I(InstarNumber^2)"),]
```

The average within-colony condition variance was also small at `r meanCondBootVar` $\pm$ `r SECondBootVar`. However, there were
significant fixed effects. The model with the lowest AIC included colony size, the two-way interaction instar age by
sex and the two-way interaction instar age squared by instar sex
`r figNumLookup$Table_models`.

Colony size had a significant effect (glmmPQR; 
$\chi$^2^~`r NSCondRes$Df`~ =
`r NSCondRes$Chisq`, p `r NSCondRes$pValue`
`r NSCondRes$stars`) as within-colony condition variance decreased with
increasing colony size `r figNumLookup$Fig_ConditionVarianceVsColSize[1]`.
Interactions of instar age or sex with colony size were not significant.


The interaction instar age by sex was significant (glmmPQR;
$\chi$^2^~`r InstarSexCondRes$Df`~ = `r InstarSexCondRes$Chisq`, p
`r InstarSexCondRes$pValue` `r InstarSexCondRes$stars`), as was instar
age squared crossed with sex (glmmPQR; $\chi$^2^~`r InstarSexSqrCondRes$Df`~ =
`r InstarSexSqrCondRes$Chisq`, p `r InstarSexSqrCondRes$pValue`
`r InstarSexSqrCondRes$stars`
`r figNumLookup$Fig_ConditionVarianceVsColSize[1]`. Within-colony variance
in condition peaked at intermediate instar ages and was higher for males 
`r figNumLookup$Fig_CondVarByInstarBoxplot[1]`.


```{r ConditionVarianceInstarGridGraph, fig.height=9, fig.width=14}
InstarGridGraph(condBootVar, "bootVarTrans", "Variance in Condition (arcsin transformed)", "n", "", varBootCondMod, "y")

figNumLookup$Fig_ConditionVarianceVsColSize

```
  
 _FIGURE : Within-colony condition variance against colony size with the
results of the generalized linear model for individual instars superimposed.
Colony size had a significant effect on condition variance
(p `r NSCondRes$pValue` `r NSCondRes$stars`)._


```{r instarCondVarianceGraph, fig.height=5, fig.width=7, echo = FALSE, dpi=300}
# graph of condition vs instar
condBootIntFormula <-  bootVarTrans ~ InstarNumber:InstarSex + InstarSex:I(InstarNumber^2)
InstarOnlyModel <- glmmPQL(condBootIntFormula, ~1|NestID, family = gaussian(link = "log"), data = condBootVar, weights = lmrWgts, niter = 10)		
#Anova(InstarOnlyModel)

# calculating the model values
predictDF <- expand.grid(InstarSex = c("F", "M"), InstarNumber = seq(4, 7, by = 0.1),  NestID = c("44.4EX12"))
predictDF$lmrPrd <- predict(InstarOnlyModel, predictDF, type = "response")

# plotting
plot <- ggplot(data = predictDF, aes(x = InstarNumber, y= lmrPrd, colour = InstarSex)) + geom_line(size = 1) + 
		scale_x_continuous(breaks=c(3,4,5,6,7, 8)) 
plot + geom_boxplot(data = condBootVar, aes(fill = InstarSex, x = InstarNumber, y = bootVarTrans, group = Instar), outlier.shape = 20, color = "black") +
		xlab("Instar Age") + ylab("Variance in Condition (arcsin transformed)") + theme_bw(base_size=10)	+ mytheme + scale_fill_grey() + scale_colour_grey()

figNumLookup$Fig_CondVarByInstarBoxplot
```

 _FIGURE :Within-colony condition variance as a function of instar age and
sex. Overlaid is the generalized linear model, which has the square of instar
age as a significant term._


### Size and condition of dispersers

```{r LegSingle, results='asis',  echo = FALSE}
##### Leg length vs colony type
FullModel <- lmer(logLeg ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
modelList$test <- c(modelList$test, "Leg length dispersed female vs. source colony")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModel))

NSModel <- lmer(logLeg ~   (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSResults <- outputResultsWord(FullModel, NSModel)
```
  
Adult female leg length was larger (lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~=
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`), 

```{r CondSingle, results='asis',  echo = FALSE}
##### condition vs colony type3
nestsToTestSig$OrigNest <- as.factor(nestsToTestSig$OrigNest)
FullModel <- lmer(condResiduals ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
modelList$test <- c(modelList$test, "Condition dispersed female vs. source colony")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModel))

NSModel <- lmer(condResiduals ~  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSResults <- outputResultsWord(FullModel, NSModel)	

nprops <- nlevels(nestsToTestSig$NestID) - nlevels(nestsToTestSig$OrigNest)
```

and their individual condition greater
(lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~=
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`),
when dispersed in propagules compared to 
adult females in their natal colonies `r figNumLookup$Fig_DispersalCondLeg[1]`.

```{r SingleGraphs, fig.height=7, fig.width=14}
p1 <- ggplot(nestsToTestSigCond, aes(x=type, y=condResiduals)) + geom_boxplot() + xlab("Colony Type") +
		ylab("Individual Condition") +  scale_x_discrete(breaks=c("multiple", "single"), labels=c("source colony", "dispersers")) +
		theme_bw(base_size=25) + mytheme

p2 <- ggplot(nestsToTestSig, aes(x=type, y=logLeg)) + geom_boxplot() + xlab("Colony Type") +
		ylab("Leg Length (log transformed)") + theme_bw(base_size=25) +
		scale_x_discrete(breaks=c("multiple", "single"), labels=c("source colony", "dispersers")) +
		mytheme

grid.arrange(p2, p1, ncol = 2)

figNumLookup$Fig_DispersalCondLeg
```
  
_FIGURE: Leg length and individual condition of adult females in propagules
compared to adult females in their natal colony following dispersal. There was a
significant difference between the two for both variables (leg lengh: stats,
condition: stats), n source colonies = 2, n propagules = `r nprops`_



Instar Age x nest size Interaction Graph
--------------------
 

```{r, fig.height=4, fig.width=6, dpi=300}

dataset <- spidersMul


FullModel <- lmer(condResiduals ~ logCtFm + InstarNumber + logCtFm:InstarNumber + (1|NestID), data = dataset, REML = FALSE)

a_predictDF <- expand.grid(logCtFm = seq(min(dataset$logCtFm), max(dataset$logCtFm), by = 0.1), 
		InstarNumber = c(4, 5, 6, 7), InstarSex = c("F"), NestID = c("44.4EX12"))


a_predictDF$lmrPrd <- predict(FullModel, a_predictDF)


a_predictDF <- ddply(a_predictDF, c("InstarNumber"), transform, minValue = min(lmrPrd))

a_predictDF$scaled <- a_predictDF$lmrPrd - a_predictDF$minValue

#ggplot(data = a_predictDF, aes(x = logCtFm, y = scaled, colour = as.factor(InstarNumber))) + geom_line(size = 1) + mytheme +
		#ylab("Scaled Predicted Condition") + xlab("Log Count Females") + scale_colour_discrete(name = "Instar Age")



ggplot(data = a_predictDF, aes(x = 10^logCtFm, y = lmrPrd, linetype = as.factor(InstarNumber))) + geom_line(size = 0.4) + mytheme +
		ylab("Predicted Individual Condition") + xlab("Colony Size (number of adult females)")+ 
		scale_x_log10(limits = c(8, 10000), breaks = c(10, 100, 1000, 10000),  labels=c("10", "100", "1000 ", "10000  ")) +
		scale_linetype_manual(name = "Instar Age", values=c(1, 2, 3, 4)) + theme(panel.background = element_blank())



```


### Single female colony survival


We found that propagules established by single females had a very low survival rate, 
with a mid-life of xx days and only a ~15% surviving to 50 days after establishment  
`r figNumLookup$Fig_progSurvival`.

```{r PropaguleSurvivalGraph, fig.height=3, fig.width=5, dpi=300}

p1 <- ggsurvplot(prop.survfit, break.time.by = 5, 
		xlab = "Days from propagule establishment", ylab = "Propagule survival probability",  censor = FALSE, 
		font.tickslab = c(8),
		font.x = c(10),
		font.y = c(10))


print(p1)

nProps <- nlevels(props$propID)
nOriginalNests <- nlevels(props$nestID)

figNumLookup$Fig_progSurvival

```
  
_FIGURE:  The survival function of `r nProps` propagules from
`r nOriginalNests` source colonies. Grey shading represents the 95% confidence
interval._


