
---
title: "Weight Vs Colony Size Results with instar as numeric"
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r docSettings, include = FALSE}
## Make sure to run R code /CurrentPaperCode_9Aug/_RUNFIRST
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, warning = FALSE)
modelList <-  list(test = c(), fullModel = c())
no_nest <- nlevels(spidersMul$NestID)

table(spiders$Instar)

rndGraphExp <- "The points represent each individuals measurement and the superimposed lines is the predicted values of full linear model for each random factor i.e. Nest ID"
	
```

### Leg length against colony size


```{r LegInstarNumber, results='asis',  echo = FALSE}
##### Leg length vs instar

FullModelLeg <- lmer(logLeg ~ logCtFm + InstarNumber + logCtFm:InstarNumber + InstarNumber:InstarSex +  
    			(1 | NestID), data = spidersMul, REML = FALSE)
modelList$test <- c(modelList$test, "Leg length vs. colony size")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModelLeg))
#testing against instar
InstarModel <- update(FullModelLeg , .~. - InstarNumber -logCtFm:InstarNumber - InstarNumber:InstarSex)
InstarResults <- outputResultsWord(FullModelLeg, InstarModel)
	
```

The final model included the two-way interaction instar age by instar sex
and colony size by instar age.

After confirming, not surprisingly, that
leg length was highly correlated with instar age 

(lmer;
$\chi$^2^~`r InstarResults[[1]]` ,`r InstarResults[[2]]`~=
`r InstarResults[[3]]`, p = `r InstarResults[[4]]` `r InstarResults[[5]]`), 



```{r LegVsNestSize, results='asis',  echo = FALSE}
##### Leg length vs nest size
NSModel <- update(FullModelLeg , .~. - logCtFm -logCtFm:InstarNumber)
NSResults <- outputResultsWord(FullModelLeg , NSModel)	
```

we found that leg length increased as colony size increased
 
(lmer; $\chi$^2^~`r NSResults[[1]]`
,`r NSResults[[2]]`~= `r NSResults[[3]]`, p = `r NSResults[[4]]`
`r NSResults[[5]]`, `r figNumLookup$Fig_LegLengthVsColonySize[1]`, 



```{r LeglogCtFmByInstarNumber, results='asis',  echo = FALSE}
##### Leg length vs logCtFm by InstarNumber interaction
Instar2IntModel <- update(FullModelLeg , .~. - logCtFm:InstarNumber)
Instar2IntResults <- outputResultsWord(FullModelLeg , Instar2IntModel)	
```

but, with a significant interaction with instar
age 

(lmer; $\chi$^2^~`r Instar2IntResults[[1]]` ,`r Instar2IntResults[[2]]`~=
`r Instar2IntResults[[3]]`, p = `r Instar2IntResults[[4]]`
`r Instar2IntResults[[5]]`)

```{r Leg3Interaction, results='asis',  echo = FALSE}
##### Leg length vs three way interaction
Instar3IntModel <- update(FullModelLeg , .~. - InstarNumber:InstarSex)
Instar3IntResults <- outputResultsWord(FullModelLeg , Instar3IntModel)	
```

and a significant interaction between instar age and
instar sex 

(lmer; $\chi$^2^~`r Instar3IntResults[[1]]`
,`r Instar3IntResults[[2]]`~= `r Instar3IntResults[[3]]`, p =
`r Instar3IntResults[[4]]` `r Instar3IntResults[[5]]`). 


```{r LegIndInstar, results='asis',  echo = FALSE}
##### Leg length vs nest size for each instar
FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, InstarNumber == 7))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, InstarNumber == 7))
AdultRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, InstarNumber == 6))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, InstarNumber == 6))
Sub2Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, InstarNumber == 5))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, InstarNumber == 5))
Sub1Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, InstarNumber ==  4))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, InstarNumber == 4))
Juv4Res <- outputResultsWord(FullModel, RedModel)

# not using
FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))
AdMaleRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))
SubMaleRes <- outputResultsWord(FullModel, RedModel)	
```

Due to the significant interaction between instar age and colony size we
performed tests on each instar individually. We found that leg length increased
with colony size in the older instars, but not significantly so in the younger
ones `r figNumLookup$Table_InstarLeg[1]` and   
`r figNumLookup$Fig_LegLengthVsColonySize[1]`.




| Instar name  | Instar Age    | $\chi$^2^ |  p value| 
|----------|----|---------------------|--------------------------------------| 
|Juvenile  |4| `r (Juv4Res[[3]])` |   `r Juv4Res[[4]]` `r Juv4Res[[5]]`  | 
| Subadult 1 |5| `r (Sub1Res[[3]])` |   `r Sub1Res[[4]]` `r Sub1Res[[5]]`  | 
| Subadult 2 |6| `r (Sub2Res[[3]])` |   `r Sub2Res[[4]]` `r Sub2Res[[5]]`  | 
|Adult |7|  `r (AdultRes[[3]])` |`r AdultRes[[4]]` `r AdultRes[[5]]`  |  


`r figNumLookup$Table_InstarLeg[1]`

TABLE: Results of separate analysis of leg length against colony size for
each instar age. Leg length increases with colony size in the
overall model

( $\chi$^2^~`r NSResults[[1]]` ,`r NSResults[[2]]`~= `r NSResults[[3]]`, 
p = `r NSResults[[4]]` `r NSResults[[5]]` ).


When tested individually the
relationship is only significant for the older instars.


```{r LegInstarGridGraph, fig.height=9, fig.width=14}
InstarGridGraph(spidersMul, "logLeg", "Leg Length - log transformed", model = FullModelLeg, same_y_axis = "leg")

figNumLookup$Fig_LegLengthVsColonySize

#class(FullModelLeg)[1]

```
  
FIGURE:  Leg length (tiba plus patella) as a function of colony size.

`r rndGraphExp`

Overall, leg length increased with colony size


()$\chi$^2^~`r NSResults[[1]]` ,`r NSResults[[2]]`~=
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`), 

but with a significant
interaction between colony size and instar age

()$\chi$^2^~`r Instar2IntResults[[1]]` ,`r Instar2IntResults[[2]]`~=
`r Instar2IntResults[[3]]`, p = `r Instar2IntResults[[4]]`
`r Instar2IntResults[[5]]`)

. When tested
individually, only the older instars exhibited a significant relationship. 
n= `r no_nest` colonies.


### Individual condition against colony size


```{r CondNS, results='asis',  echo = FALSE}
##### conditionh vs colony size
FullModel <- lmer(condResiduals ~  logCtFm + InstarNumber  +  (1|NestID), data = spidersMul, REML = FALSE)
modelList$test <- c(modelList$test, "Condition vs. colony size")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModel))

NSModel <- update(FullModel, ~ . - logCtFm)
NSResults <- outputResultsWord(FullModel, NSModel)

```

The final linear model for individual condition did not include any interaction
effects. 


The effect of colony size was significant 

(lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~ =
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`)

 
with individual condition decreasing as colony size increased `r figNumLookup$Fig_ConditionVsColSize`.

```{r ConditionInstar, results='asis',  echo = FALSE}
# condition vs logCtFm by instar number interaction
IntModel <- update(FullModel, . ~ . - InstarNumber)
IntResults <- outputResultsWord(FullModel, IntModel)		
```

, as was instar age (lmer; $\chi$^2^~`r IntResults[[1]]`,
`r IntResults[[2]]`~ = `r IntResults[[3]]`, p = `r IntResults[[4]]`
`r IntResults[[5]]`), with condition decreasing slighly as instar age increases.



```{r ConditionInstarGridGraph, fig.height=9, fig.width=14}

InstarGridGraph(spidersMul, "condResiduals", "Individual Condition", model = FullModel, same_y_axis = "y")

figNumLookup$Fig_ConditionVsColSize

#ggplot(spidersMul, aes(as.factor(InstarNumber), condResiduals)) + geom_boxplot()
```
  
FIGURE : Individual condition against colony size. `r cat(rndGraphExp)`.
Overall condition decreases with colony size 

( $\chi$^2^~`r NSResults[[1]]`, `r NSResults[[2]]`~ = `r NSResults[[3]]`, 
p =`r NSResults[[4]]` `r NSResults[[5]]`)




### Within-colony variance against colony size

#### Leg length size disparity

```{r LegVariacne, echo = FALSE}

meanLegBootVar <- round(mean(legBootVar$bootSD_var),2)
SELegBootVar  <- round(sd(legBootVar$bootSD_var)/sqrt(length(legBootVar$bootSD_var)), 2)

```
There was no significant effect of nest size on within-colony disparity in leg length. 
However, the average within-colony disparity in leg length was


`r meanLegBootVar` $\pm$ `r SELegBootVar`, 


which is small given that the range of possible values is between zero and one,
where zero means complete uniformity in leg length.

#### Body condition disparity

```{r CondVariance, results='asis',  echo = FALSE, message = FALSE, warning = FALSE}
# mean and SD
meanCondBootVar <- round(mean(condBootVar$bootSD_var), 2)
SECondBootVar  <- round(sd(condBootVar$bootSD_var)/sqrt(length(legBootVar$bootSD_var)),2)

# formatting the data
totSpis<- sum(condBootVar$N)
condBootVar$lmrWgts <- condBootVar$N/totSpis
condBootVar$bootVarTrans <- asin(sqrt(condBootVar$bootSD_var))
condBootVar$bootVarTrans <- condBootVar$bootVarTrans*100 # Making variance a percentage
condBootVar$bootVarTrans <- condBootVar$bootVarTrans +1 # have to add a small amount or glmer "can't find starting values"

# running the model
condBootFormula <-  bootVarTrans ~ logCtFm + InstarNumber + 
		InstarNumber:InstarSex + I(InstarNumber^2)
varBootCondMod <- glmmPQL(condBootFormula, ~1|NestID, family = gaussian(link = "log"), data = condBootVar, 
		weights = lmrWgts, niter = 10)


#modelList$test <- c(modelList$test, "Condition Variance vs. colony size")
#modelList$fullModel <- c(modelList$fullModel, docxFmula(condBootFormula))

# testing with wald test


NSCondRes <- waldDoc_fun(varBootCondMod, 2)

```

The average within-colony condition disparity was also small at 

`r meanCondBootVar` $\pm$ `r SECondBootVar`. 

However, there were
significant fixed effects. 

The final model included the square of instar age and the two way the
interaction instar age by instar.


Colony size had a significant effect 


(glmmPQR; 
$\chi$^2^~`r NSCondRes[['df']]`~ =
`r NSCondRes[['chi2']]`, p = `r NSCondRes[['P']]`
`r NSCondRes[['stars']]`) 


as within-colony body condition disparity decreased with
increasing colony size `r figNumLookup$Fig_ConditionVarianceVsColSize[1]`.


```{r CondVarianceInt, results='asis',  echo = FALSE, message = FALSE, warning = FALSE}

InstarSexCondRes <- waldDoc_fun(varBootCondMod, 5)

```



The interaction instar age by sex was significant 

(glmmPQR; $\chi$^2^~`r InstarSexCondRes[['df']]`~ =
`r InstarSexCondRes[['chi2']]`, p = `r InstarSexCondRes[['P']]`
`r InstarSexCondRes[['stars']]`), 



```{r CondVarianceInt2, results='asis',  echo = FALSE, message = FALSE, warning = FALSE}

InstarSexSqrCondRes <-  waldDoc_fun(varBootCondMod, 4)

```

as was instar age squared

(glmmPQR; $\chi$^2^~`r InstarSexSqrCondRes[['df']]`~ =
`r InstarSexSqrCondRes[['chi2']]`, p = `r InstarSexSqrCondRes[['P']]`
`r InstarSexSqrCondRes[['stars']]`
`r figNumLookup$Fig_ConditionVarianceVsColSize[1]`). 


Within-colony variance
in condition peaked at intermediate instar ages and was higher for males 
`r figNumLookup$Fig_CondVarByInstarBoxplot[1]`.


```{r ConditionVarianceInstarGridGraph, fig.height=9, fig.width=14}

condBootVar$bootSD_varProp <- condBootVar$bootVarTrans/100


condBootFormula <-  bootVarTrans ~ logCtFm + InstarNumber + 
		InstarNumber:InstarSex + I(InstarNumber^2) + I(InstarNumber^2):InstarNumber +
		I(InstarNumber^2):InstarNumber:InstarSex
		


varBootCondMod <- glmmPQL(condBootFormula, ~1|NestID, family = gaussian(link = "log"), data = condBootVar, 
		weights = lmrWgts, niter = 10)

InstarGridGraph(condBootVar, "bootSD_varProp", "Body condition disparity", model = varBootCondMod, same_y_axis = "y")



#condBootVar$lmrPrd <- predict(varBootCondMod, condBootVar, type = "response")

#ggplot(condBootVar, aes(logCtFm, lmrPrd/100, colour = Instar)) + geom_point()

#lmrPrd/100

figNumLookup$Fig_ConditionVarianceVsColSize

```
  
 _FIGURE : Within-colony condition disparity (asin transformed) against colony size with the
results of the generalized linear model for individual instars superimposed.
Colony size had a significant effect on condition variance
(p = `r NSCondRes[['P']]` `r NSCondRes[['stars']]`)._


```{r instarCondVarianceGraph, fig.height=5, fig.width=7, echo = FALSE, dpi=300}
# graph of condition vs instar
condBootIntFormula <-  bootVarTrans ~ InstarNumber:InstarSex + InstarSex:I(InstarNumber^2)
InstarOnlyModel <- glmmPQL(condBootIntFormula, ~1|NestID, family = gaussian(link = "log"), data = condBootVar, weights = lmrWgts, niter = 10)		
#Anova(InstarOnlyModel)

# calculating the model values
predictDF <- expand.grid(InstarSex = c("F", "M"), InstarNumber = seq(4, 7, by = 0.1),  NestID = c("44.4EX12"))
predictDF$lmrPrd <- predict(InstarOnlyModel, predictDF, type = "response")
predictDF$lmrPrd <- predictDF$lmrPrd/100

# plotting
plot <- ggplot(data = predictDF, aes(x = InstarNumber, y= lmrPrd, colour = InstarSex)) + geom_line(size = 1) + 
		scale_x_continuous(breaks=c(3,4,5,6,7, 8)) 
plot + geom_boxplot(data = condBootVar, aes(fill = InstarSex, x = InstarNumber, y = bootVarTrans/100, group = Instar), outlier.shape = 20, color = "black") +
		xlab("Instar Age") + ylab("Body condition disparity") + theme_bw(base_size=10)	+ mytheme + scale_fill_grey() + scale_colour_grey()

figNumLookup$Fig_CondVarByInstarBoxplot
```

 _FIGURE :Within-colony condition variance as a function of instar age and
sex. Overlaid is the generalized linear model, which has the square of instar
age as a significant term  $\chi$^2^~`r InstarSexSqrCondRes[['df']]`~ =
`r InstarSexSqrCondRes[['chi2']]`, p = `r InstarSexSqrCondRes[['P']]`
`r InstarSexSqrCondRes[['stars']]`
`r figNumLookup$Fig_ConditionVarianceVsColSize[1]`.




### Size and condition of dispersers

```{r LegSingle, results='asis',  echo = FALSE}
##### Leg length vs colony type
FullModel <- lmer(logLeg ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
modelList$test <- c(modelList$test, "Leg length dispersed female vs. source colony")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModel))

NSModel <- lmer(logLeg ~   (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSResults <- outputResultsWord(FullModel, NSModel)
```
  
Adult female leg length was larger (lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~=
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`), 

```{r CondSingle, results='asis',  echo = FALSE}
##### condition vs colony type3
nestsToTestSig$OrigNest <- as.factor(nestsToTestSig$OrigNest)
FullModel <- lmer(condResiduals ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
modelList$test <- c(modelList$test, "Condition dispersed female vs. source colony")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModel))

NSModel <- lmer(condResiduals ~  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSResults <- outputResultsWord(FullModel, NSModel)	

nprops <- nlevels(nestsToTestSig$NestID) - nlevels(nestsToTestSig$OrigNest)
```

and their individual condition greater

(lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~=
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`),

when dispersed in propagules compared to 
adult females in their natal colonies `r figNumLookup$Fig_DispersalCondLeg[1]`.

```{r SingleGraphs, fig.height=7, fig.width=14}
p1 <- ggplot(nestsToTestSigCond, aes(x=type, y=condResiduals)) + geom_boxplot() + xlab("Colony Type") +
		ylab("Individual Condition") +  scale_x_discrete(breaks=c("multiple", "single"), labels=c("source colony", "dispersers")) +
		theme_bw(base_size=25) + mytheme

p2 <- ggplot(nestsToTestSig, aes(x=type, y=logLeg)) + geom_boxplot() + xlab("Colony Type") +
		ylab("Leg Length (log transformed)") + theme_bw(base_size=25) +
		scale_x_discrete(breaks=c("multiple", "single"), labels=c("source colony", "dispersers")) +
		mytheme

grid.arrange(p2, p1, ncol = 2)

figNumLookup$Fig_DispersalCondLeg
```
  
_FIGURE: Leg length and individual condition of adult females in propagules
compared to adult females in their natal colony following dispersal. There was a
significant difference between the two for both variables (leg lengh: stats,
condition: stats), n source colonies = 2, n propagules = `r nprops`_



Instar Age x nest size Interaction Graph
--------------------
 

```{r, fig.height=4, fig.width=6, dpi=300}

dataset <- spidersMul


FullModel <- lmer(condResiduals ~ logCtFm + InstarNumber + logCtFm:InstarNumber + (1|NestID), data = dataset, REML = FALSE)

a_predictDF <- expand.grid(logCtFm = seq(min(dataset$logCtFm), max(dataset$logCtFm), by = 0.1), 
		InstarNumber = c(4, 5, 6, 7), InstarSex = c("F"), NestID = c("44.4EX12"))


a_predictDF$lmrPrd <- predict(FullModel, a_predictDF)


a_predictDF <- ddply(a_predictDF, c("InstarNumber"), transform, minValue = min(lmrPrd))

a_predictDF$scaled <- a_predictDF$lmrPrd - a_predictDF$minValue

#ggplot(data = a_predictDF, aes(x = logCtFm, y = scaled, colour = as.factor(InstarNumber))) + geom_line(size = 1) + mytheme +
		#ylab("Scaled Predicted Condition") + xlab("Log Count Females") + scale_colour_discrete(name = "Instar Age")



ggplot(data = a_predictDF, aes(x = 10^logCtFm, y = lmrPrd, linetype = as.factor(InstarNumber))) + geom_line(size = 0.4) + mytheme +
		ylab("Predicted Individual Condition") + xlab("Colony Size (number of adult females)")+ 
		scale_x_log10(limits = c(8, 10000), breaks = c(10, 100, 1000, 10000),  labels=c("10", "100", "1000 ", "10000  ")) +
		scale_linetype_manual(name = "Instar Age", values=c(1, 2, 3, 4)) + theme(panel.background = element_blank())



```


### Single female colony survival


We found that propagules established by single females had a very low survival rate, 
with a mid-life of 37 days and only a ~15% surviving to 50 days after
establishment  
`r figNumLookup$Fig_progSurvival`.

```{r PropaguleSurvivalGraph, fig.height=3, fig.width=5, dpi=300}

p1 <- ggsurvplot(prop.survfit, break.time.by = 5, 
		xlab = "Days from propagule establishment", ylab = "Propagule survival probability",  censor = FALSE, 
		font.tickslab = c(8),
		font.x = c(10),
		font.y = c(10),
		palette = "gray",
		colour = "black",
		legend = "none")


print(p1)

nProps <- nlevels(props$propID)
nOriginalNests <- nlevels(props$nestID)

figNumLookup$Fig_progSurvival

```
  
_FIGURE:  The survival function of `r nProps` propagules from
`r nOriginalNests` source colonies. Grey shading represents the 95% confidence
interval._


