---
title: "`r student`: Draft Ignite Talk Feedback&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Mark: `r mark` /10"
output:
  word_document:
    reference_docx: FormatReferenceDoc.docx
---


```{r docSettings, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.height=3, fig.width=5)

```

`r title_date` 2017 -  `r title`
===


----------

#_Students' Talk Summary_
 
```{r StudentSummaries, results='asis', echo=FALSE, tidy=FALSE}

cat(data_table$StudentSumm[row_num])
```


#_Student Survey Feedback_

###Did the talk flow logically and was the purpose of the talk achieved? 

```{r Flow, fig.height=4, fig.width=5}
Flow_opt <-c("Yes", "Reordering the sections\nwould help", "Struggled to understand\nrelevance of some sections", 
"Too much information", "Didn't understand the\npurpose of the talk",
"Too much jargon")
		

Flow_results <- c(data_table$Flow_yes[row_num], data_table$Flow_reorder[row_num], data_table$Flow_struuggled[row_num], 
data_table$Flow_Overwhelming[row_num], data_table$Flow_noUnderstand[row_num], data_table$Flow_jargon[row_num])

Flow_table <- data.frame(Flow_opt = as.factor(Flow_opt), Flow_results)

ggplot(Flow_table, aes(x = Flow_opt, y =Flow_results, fill = Flow_opt)) + geom_bar(stat="identity") + 
		xlab("") + ylab(ylabel) + theme_bw() + 
		theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line=element_line(), legend.position="none", axis.text.x=element_text(angle=45, hjust= 1.1))

		
```


###Question: Did you understand the significance of the main research paper?

```{r Paper, fig.height=3, fig.width=3.5}
Paper_opt <- c("Yes", "Kinda", "No", "What research\npaper?")
		
Paper_results <- c(data_table$Paper_yes[row_num], data_table$Paper_Kinda[row_num], data_table$Paper_No[row_num],
data_table$Paper_what[row_num])

Paper_table <- data.frame(Paper_opt = as.factor(Paper_opt), Paper_results)

ggplot(Paper_table, aes(x = Paper_opt, y = Paper_results, fill = Paper_opt)) + geom_bar(stat="identity") + 
		xlab("") + ylab(ylabel) + theme_bw() + 
		theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line=element_line(), legend.position="none", axis.text.x=element_text(angle=45, hjust= 1.1))
		
```



###How interesting and important did you find the topic?

```{r Topic, fig.height=3.5, fig.width=4}
Topic_opt <- c("Very", " Important, but\ninformation not new", "Informative, but the\nimportance wasn't clear", 
"Not very important\nor informative")
		
Topic_results <- c(data_table$Topic_very[row_num], data_table$Topic_Important[row_num], data_table$Topic_Informative[row_num],
data_table$Topic_not[row_num])

Topic_table <- data.frame(Topic_opt = as.factor(Topic_opt), Topic_results)

ggplot(Topic_table, aes(x = Topic_opt, y = Topic_results, fill = Topic_opt)) + geom_bar(stat="identity") + 
		xlab("") + ylab(ylabel) + theme_bw() + 
		theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line=element_line(), legend.position="none", axis.text.x=element_text(angle=45, hjust= 1.1))
		
```


###Was the narration synchronized with the slides?

```{r Narration, fig.height=3, fig.width=3.5}
Narration_opt <- c("Yes, nicely", "Yes, but rushed", "OK, except\nat the end", "Only at\nthe start")
		
Narration_results <- c(data_table$Talk_yes[row_num], data_table$Talk_rushed[row_num], data_table$Talk_OK[row_num],
data_table$Talk_start[row_num])

Narration_table <- data.frame(Narration_opt = as.factor(Narration_opt), Narration_results)

ggplot(Narration_table, aes(x = Narration_opt, y = Narration_results, fill = Narration_opt)) + geom_bar(stat="identity") + 
		xlab("") + ylab(ylabel) + theme_bw() + 
		theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line=element_line(), legend.position="none", axis.text.x=element_text(angle=45, hjust= 1.1))
		
```

###Did you understand the point of each slide and/or image?

```{r Slides, fig.height=3, fig.width=3}
Slides_opt <- c("Clear", "Vague", "Not described")
		
Slides_results <- c(data_table$Slides_yes[row_num], data_table$Slides_most[row_num], data_table$Slides_some[row_num])

Slides_table <- data.frame(Slides_opt = as.factor(Slides_opt), Slides_results)

ggplot(Slides_table, aes(x = Slides_opt, y = Slides_results, fill = Slides_opt)) + geom_bar(stat="identity") + 
		xlab("") + ylab(ylabel) + theme_bw() + 
		theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line=element_line(), legend.position="none", axis.text.x=element_text(angle=45, hjust= 1.1))
```


###Did you have time to read the information in each slide? 
```{r SlideInfo, fig.height=3, fig.width=3.5}
SlideInfo_opt <- c("Yes", "Most of them", "Only Some", "Irrelevant or\ndistracting")
		
SlideInfo_results <- c(data_table$SlideInfo_yes[row_num], data_table$SlideInfo_most[row_num], 
data_table$SlideInfo_some[row_num], data_table$SlideInfo_Irrel[row_num])

SlideInfo_table <- data.frame(SlideInfo_opt = as.factor(SlideInfo_opt), SlideInfo_results)

ggplot(SlideInfo_table, aes(x = SlideInfo_opt, y = SlideInfo_results, fill = SlideInfo_opt)) + geom_bar(stat="identity") + 
		xlab("") + ylab(ylabel) + theme_bw() + 
		theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line=element_line(), legend.position="none", axis.text.x=element_text(angle=45, hjust= 1.1))
		
```

##Comments from Ruth

```{r RuthComments, results='asis', echo=FALSE, tidy=FALSE}

cat(data_table$RuthComments[row_num])
```


##Comments from Rosie

##Comments from students

```{r StudentComments, results='asis', echo=FALSE, tidy=FALSE}
cat(data_table$StudentComments[row_num])
```
