
---
title: "Weight Vs Colony Size Results with instar as numeric"
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r docSettings, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE)
modelList <-  list(test = c(), fullModel = c())
no_nest <- nlevels(spidersMul$NestID)

table(spiders$Instar)
	
```

Count of number of spiders
-----
```{r CountOfSpiders}

xtable(table(spiders$Instar))

```


Leg Vs. Colony Size
--------------------

```{r LegInstarNumber, results='asis',  echo = FALSE}
##### Leg length vs instar

FullModelLeg <- lmer(logLeg ~ logCtFm + InstarNumber + logCtFm:InstarNumber + logCtFm:InstarNumber:InstarSex +  
    			(1 | NestID), data = spidersMul, REML = FALSE)
modelList$test <- c(modelList$test, "Leg length")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModelLeg ))

#testing against instar
InstarModel <- update(FullModelLeg , .~. - InstarNumber -logCtFm:InstarNumber - logCtFm:InstarNumber:InstarSex)
InstarResults <- outputResultsWord(FullModelLeg, InstarModel)
	
```

The model with the lowest AIC value included the two-way interaction 
colony size by instar age and the 
three-way interaction colony size by instar age by instar sex as fixed effects,
but did not include the instar age by instar sex interaction.
After confirming, not surprisingly, that leg length was significantly correlated with instar age
(lmer; $\chi$^2^~`r InstarResults[[1]]`
,`r InstarResults[[2]]`~= `r InstarResults[[3]]`, p = `r InstarResults[[4]]`
`r InstarResults[[5]]`), we found that

```{r LegVsNestSize, results='asis',  echo = FALSE}
##### Leg length vs nest size
NSModel <- update(FullModelLeg , .~. - logCtFm -logCtFm:InstarNumber - logCtFm:InstarNumber:InstarSex)
NSResults <- outputResultsWord(FullModelLeg , NSModel)	
```

leg length increased increases as colony size increased 
(lmer; $\chi$^2^~`r NSResults[[1]]`
,`r NSResults[[2]]`~= `r NSResults[[3]]`, p = `r NSResults[[4]]`
`r NSResults[[5]]`, figure 1), 

```{r LeglogCtFmByInstarNumber, results='asis',  echo = FALSE}
##### Leg length vs logCtFm by InstarNumber interaction
Instar2IntModel <- update(FullModelLeg , .~. - logCtFm:InstarNumber - logCtFm:InstarNumber:InstarSex)
Instar2IntResults <- outputResultsWord(FullModelLeg , Instar2IntModel)	
```

but there is a significant two-way interaction between colony size and instar
age (lmer; $\chi$^2^~`r Instar2IntResults[[1]]` ,`r Instar2IntResults[[2]]`~=
`r Instar2IntResults[[3]]`, p = `r Instar2IntResults[[4]]`
`r Instar2IntResults[[5]]`)

```{r Leg3Interaction, results='asis',  echo = FALSE}
##### Leg length vs three way interaction
Instar3IntModel <- update(FullModelLeg , .~. - logCtFm:InstarNumber:InstarSex)
Instar3IntResults <- outputResultsWord(FullModelLeg , Instar3IntModel)	
```

 and a significant three-way interaction between colony size, instar age and
instar sex (lmer; $\chi$^2^~`r Instar3IntResults[[1]]`
,`r Instar3IntResults[[2]]`~= `r Instar3IntResults[[3]]`, p =
`r Instar3IntResults[[4]]` `r Instar3IntResults[[5]]`). 


```{r LegIndInstar, results='asis',  echo = FALSE}
##### Leg length vs nest size for each instar
FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
AdultRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Sub2"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Sub2"))
Sub2Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Sub1"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Sub1"))
Sub1Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Juv4"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Juv4"))
Juv4Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))
AdMaleRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))
SubMaleRes <- outputResultsWord(FullModel, RedModel)	
```

Performing tests on each instar individually, we found that leg length increased with colony size in the older instars, but not significantly so in the younger ones (Table 1, figure 1).

*Table 1: Results of post-hoc analysis of leg length against colony size for
each instar. Leg length increases as colony size increases, but when tested
individually is significant only for the older instars.*


| Instar   | Instar Age    | $\chi$^2^ |  p value| 
|----------|----|---------------------|--------------------------------------| 
|Juv4 |4| `r (Juv4Res[[3]])` |   `r Juv4Res[[4]]` `r Juv4Res[[5]]`  | 
| Sub1 Female|5| `r (Sub1Res[[3]])` |   `r Sub1Res[[4]]` `r Sub1Res[[5]]`  | 
| Sub2 Female|6| `r (Sub2Res[[3]])` |   `r Sub2Res[[4]]` `r Sub2Res[[5]]`  | 
|Adult Female |7|  `r (AdultRes[[3]])` |`r AdultRes[[4]]` `r AdultRes[[5]]`  |  
|Sub Male|5| `r (SubMaleRes[[3]])` |`r SubMaleRes[[4]]` `r SubMaleRes[[5]]`|
|Adult Male |6| `r (AdMaleRes[[3]])` |`r AdMaleRes[[4]]` `r AdMaleRes[[5]]` | 




```{r LegInstarGridGraph, fig.height=9, fig.width=14}
InstarGridGraph(spidersMul, "logLeg", "Leg Length - log transformed", "n", "", FullModelLeg)
```
  
(@) _Figure:  Leg length against colony size. Overall leg length increased with_
_colony size (p = `r NSResults[[4]]` `r NSResults[[5]]`), but only for the
older instars (there was a significant interaction between colony size and instar(p =
`r InstarResults[[4]]` `r InstarResults[[5]]`), n = `r no_nest` colonies._


Condition Vs. Colony Size
--------------------

```{r CondNS, results='asis',  echo = FALSE}
##### conditionh vs colony size
FullModel <- lmer(condResiduals ~  logCtFm + logCtFm:InstarNumber  +  (1|NestID), data = spidersMul, REML = FALSE)
modelList$test <- c(modelList$test, "Condition")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModel))

NSModel <- update(FullModel, ~ . - logCtFm - logCtFm:InstarNumber)
NSResults <- outputResultsWord(FullModel, NSModel)

```
The model with the lowest AIC included only one interaction term, instar age by colony size, and it 
did not include instar sex or instar age as fixed effects. Colony size was significant (lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~ =
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`) with condition decreasing as colony size increased (figure 2).

```{r ConditionInteraction, results='asis',  echo = FALSE}
# condition vs logCtFm by instar number interaction
IntModel <- update(FullModel, . ~ . - logCtFm:InstarNumber)
IntResults <- outputResultsWord(FullModel, IntModel)		
```

There was a significant interaction between instar age
 and colony size (lmer; $\chi$^2^~`r IntResults[[1]]`, `r IntResults[[2]]`~ =
`r IntResults[[3]]`, p = `r IntResults[[4]]` `r IntResults[[5]]`), with condition appearing to decrease at a faster rate 
with colony size as the instar age 
increases (figure 3).

```{r ConditionAdultOnly, results='asis',  echo = FALSE}
# Only adult significant post-hoc
FullModelAdOnly <- lmer(condResiduals ~  logCtFm +  (1|NestID), data = subset(spidersMul, Instar == "Adult"), REML = FALSE)
RedModAd <- update(FullModelAdOnly, .~. - logCtFm)
AdultResults <- outputResultsWord(FullModelAdOnly, RedModAd)
```

However, when performing tests on the instars individually we found that only
adult female condition decreased significantly with colony size (lmer;
$\chi$^2^~`r AdultResults[[1]]`, `r AdultResults[[2]]`~ = `r AdultResults[[3]]`,
p = `r AdultResults[[4]]` `r AdultResults[[5]]`).

```{r ConditionInstarGridGraph, fig.height=9, fig.width=14}
InstarGridGraph(spidersMul, "condResiduals", "Individual Condition", "n", "", FullModel, "y")
```
  
(@)  _Figure : Individual condition against colony size. Overall condition
decreases with colony size (p = `r NSResults[[4]]` `r NSResults[[5]]`), with
 a significant interaction with instar(p = `r InstarResults[[4]]`
`r InstarResults[[5]]`)._

```{r InstarConditionInteractionGraph, fig.height=3.5, fig.width=5.5, dpi=300}
#nest size by condition - instar interaction graph
a_predictDF <- expand.grid(logCtFm = seq(min(spidersMul$logCtFm), max(spidersMul$logCtFm), by = 0.1), 
		InstarNumber = c(4, 5, 6, 7), NestID = c("44.4EX12"))
a_predictDF$lmrPrd <- predict(FullModel, a_predictDF)
ggplot(data = a_predictDF, aes(x = logCtFm, y = lmrPrd, colour = as.factor(InstarNumber))) + geom_line(size =0.5) +
		ylab("Predicted Condition") + xlab("Log Count Females") + scale_colour_discrete(name = "Instar Age") + theme_bw(base_size=11) + mytheme



```

(@)  _Figure : The results of the linear model showing individual condition of
each instar age against colony size with both sexes combined as instar sex was
insignificant. However, when testing each instar individually, only the adult female
condition change with nest size had a significant effect (p = `r AdultResults[[4]]` `r AdultResults[[5]]`), n = `r no_nest`
colonies._



Within Colony Variance Vs. colony size
--------------------

### Leg Length Variance

```{r LegVariacne, echo = FALSE}

meanLegBootVar <- round(mean(legBootVar$bootSD_var),2)
SELegBootVar  <- round(sd(legBootVar$bootSD_var)/sqrt(length(legBootVar$bootSD_var)), 2)

```
There was no significant effect of nest size on within colony variance in leg, but the average leg variance was
`r meanLegBootVar` $\pm$ `r SELegBootVar`, which is small as the possible values the boot strap variance could take
are between zero to one.


### Condition Variance

```{r CondVariance, results='asis',  echo = FALSE, message = FALSE, warning = FALSE}
# mean and SD
meanCondBootVar <- round(mean(condBootVar$bootSD_var), 2)
SECondBootVar  <- round(sd(condBootVar$bootSD_var)/sqrt(length(legBootVar$bootSD_var)),2)

# formatting the data
totSpis<- sum(condBootVar$N)
condBootVar$lmrWgts <- condBootVar$N/totSpis
condBootVar$bootVarTrans <- asin(sqrt(condBootVar$bootSD_var))
condBootVar$bootVarTrans <- condBootVar$bootVarTrans*100 # Making variance a percentage
condBootVar$bootVarTrans <- condBootVar$bootVarTrans +1 # have to add a small amount or glmer "can't find starting values"

# running the model
condBootFormula <-  bootVarTrans ~ logCtFm + InstarNumber:InstarSex + InstarSex:I(InstarNumber^2)
varBootCondMod <- glmmPQL(condBootFormula, ~1|NestID, family = gaussian(link = "log"), data = condBootVar, weights = lmrWgts, niter = 10)		
varBootCondAnova <- addStarsOnly_anova(varBootCondMod)
modelList$test <- c(modelList$test, "Condition Variance")
modelList$fullModel <- c(modelList$fullModel, docxFmula(condBootFormula))

# seperating the results for easier printing below
NSCondRes <- varBootCondAnova[which(varBootCondAnova$parameters == "logCtFm"),]
InstarSexCondRes <- varBootCondAnova[which(varBootCondAnova$parameters == "InstarNumber:InstarSex"),]
InstarSexSqrCondRes <- varBootCondAnova[which(varBootCondAnova$parameters == "InstarSex:I(InstarNumber^2)"),]
```

In contrast, there were significant effects of colony size on within-colony condition variance. 
The average within-colony condition variance was `r meanCondBootVar` $\pm$ `r SECondBootVar`, which again is low. 
The final model included only colony size, the two-way interaction instar age by
sex interaction and the two-way interaction instar age squared by instar sex.
Colony size was significant (glmmPQR; $\chi$^2^~`r NSCondRes$Df`~ =
`r NSCondRes$Chisq`, p `r NSCondRes$pValue` `r NSCondRes$stars`) as
within-colony condition variance decreased with increasing colony size (figure 4).

The interaction instar age by sex was significant (glmmPQR;
$\chi$^2^~`r InstarSexCondRes$Df`~ = `r InstarSexCondRes$Chisq`, p
`r InstarSexCondRes$pValue` `r InstarSexCondRes$stars`, figure 5), as was instar
age squared crossed with sex (glmmPQR; $\chi$^2^~`r InstarSexSqrCondRes$Df`~ =
`r InstarSexSqrCondRes$Chisq`, p `r InstarSexSqrCondRes$pValue`
`r InstarSexSqrCondRes$stars`, figure 5). The within-colony variance in
condition peaked at intermediate instar ages and being larger for males (figure 5).
However, doing post-hoc analysis we found that none of the instars were
significant when tested individually.

```{r ConditionVarianceInstarGridGraph, fig.height=9, fig.width=14}
InstarGridGraph(condBootVar, "bootVarTrans", "Variance in Condition", "n", "", varBootCondMod, "y")

```
  
(@)  _Figure : Transformed bootstrap calculated variance in condition against colony size with the linear model
superimposed , n = `r no_nest` colonies._


```{r instarCondVarianceGraph, fig.height=3.5, fig.width=5, echo = FALSE, dpi=300}
# graph of condition vs instar
condBootIntFormula <-  bootVarTrans ~ InstarNumber:InstarSex + InstarSex:I(InstarNumber^2)
InstarOnlyModel <- glmmPQL(condBootIntFormula, ~1|NestID, family = gaussian(link = "log"), data = condBootVar, weights = lmrWgts, niter = 10)		
#Anova(InstarOnlyModel)

# calculating the model values
predictDF <- expand.grid(InstarSex = c("F", "M"), InstarNumber = seq(4, 7, by = 0.1),  NestID = c("44.4EX12"))
predictDF$lmrPrd <- predict(InstarOnlyModel, predictDF, type = "response")

# plotting
plot <- ggplot(data = predictDF, aes(x = InstarNumber, y= lmrPrd, colour = InstarSex)) + geom_line(size = 1) + 
		scale_x_continuous(breaks=c(3,4,5,6,7, 8)) 
plot + geom_boxplot(data = condBootVar, aes(x = InstarNumber, y = bootVarTrans, group = Instar, fill = InstarSex), outlier.shape = 20, color = "black") +
		xlab("Instar Age") + ylab("Variance in Condition") + theme_bw(base_size=10)	+ mytheme


```

(@) _Figure :Within-colony condition variance by instar. Overlaid
is the linear model with a significant quadratic term._


Original Colony Vs Propagule
============

```{r LegSingle, results='asis',  echo = FALSE}
##### Leg length vs colony type
FullModel <- lmer(logLeg ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
modelList$test <- c(modelList$test, "Single nest leg")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModel))

NSModel <- lmer(logLeg ~   (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSResults <- outputResultsWord(FullModel, NSModel)
```
  
Adult female leg length was larger in propagules compared to their source
colony (lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~=
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`), 

```{r CondSingle, results='asis',  echo = FALSE}
##### condition vs colony type3
nestsToTestSig$OrigNest <- as.factor(nestsToTestSig$OrigNest)
FullModel <- lmer(condResiduals ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
modelList$test <- c(modelList$test, "Single nest condition")
modelList$fullModel <- c(modelList$fullModel, docxFmula(FullModel))

NSModel <- lmer(condResiduals ~  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSResults <- outputResultsWord(FullModel, NSModel)	

nprops <- nlevels(nestsToTestSig$NestID) - nlevels(nestsToTestSig$OrigNest)
```
as was individual condition (lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~=
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`), with those in
propagules having longer legs and greater condition compared to those in the source colony.

```{r SingleGraphs, fig.height=7, fig.width=14}
p1 <- ggplot(nestsToTestSigCond, aes(x=type, y=condResiduals)) + geom_boxplot() + xlab("Colony Type") +
		ylab("Individual Condition") +  scale_x_discrete(breaks=c("multiple", "single"), labels=c("source: multiple", "propagules: single")) +
		theme_bw(base_size=25) + mytheme

p2 <- ggplot(nestsToTestSig, aes(x=type, y=logLeg)) + geom_boxplot() + xlab("Colony Type") +
		ylab("Leg Length (log transformed)") + theme_bw(base_size=25) +
		scale_x_discrete(breaks=c("multiple", "single"), labels=c("source: multiple", "propagules: single")) +
		mytheme

grid.arrange(p1, p2, ncol = 2)
```
  
(@) _Figure: Condition and leg length of adult females in propagues compared to
adult females in their source colony. Both were significant, n source colonies
= 2, n propagules = `r nprops`_


Propagule survival
--------------------

We found that colonies with single female spiders had a very low survival rate,
with there being only around a 15% chance that the single colony would survive
to 50 days after establishment (figure 7).

```{r PropaguleSurvivalGraph, fig.height=3, fig.width=5, dpi=300}

p1 <- ggsurvplot(prop.survfit, break.time.by = 5, 
		xlab = "Days from propagule establishment", ylab = "Propagule survival probability",  censor = FALSE, 
		font.tickslab = c(8),
		font.x = c(10),
		font.y = c(10))


print(p1)

nProps <- nlevels(props$propID)
nOriginalNests <- nlevels(props$nestID)

```
  
(@) _Figure:  The survival function of `r nProps` propagules from
`r nOriginalNests` source colonies. The grey shading is the 95% confidence
interval._

List of full models used
-----------------------


```{r ModelTableForLA, results = 'asis'}

modelDF <- as.data.frame(modelList)
#kable(modelDF, format = 'markdown')
pander(modelDF, split.cell = 70, split.table = Inf)


```