

---
title: "Individual Condition vs Nest Size with sex and instar as numeric value"
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: true
geometry: margin=1.5cm
header-includes:
    - \usepackage{caption}
---

\captionsetup[table]{labelformat=empty}

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE)
	
```

AIC Values of all possible models with instar always included
====================

note: InstarNumber is numeric

```{r kable, results='asis',  echo = FALSE, warnings = FALSE, message = FALSE}

dataset <- spidersMul


outcome    <- c("condResiduals")
predictors <- c("InstarNumber", "InstarNumber:InstarSex", "logCtFm:InstarNumber", "logCtFm:InstarNumber:InstarSex")

modTable <- allModelsAICWithSex(outcome, predictors, dataset)

lowestAICMod <- as.character(modTable$model[1])
formula    <- as.formula(lowestAICMod)
FullModel    <- lmer(formula, data = dataset, REML = FALSE)


row.names(modTable) <- NULL # removing row names

panderOptions('table.split.table', Inf)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('keep.line.breaks', TRUE)


pander(modTable,  row.names = NULL, justify = 'left', split.cells = c(1, 2, 61, 2))


lowestAICMod <- as.character(modTable$model[1])

formula    <- as.formula(lowestAICMod)
FullModel       <- lmer(formula, data = dataset, REML = FALSE)


	
```

\pagebreak

Checking full model fit
--------------------


```{r ModelFit, fig.height=4, fig.width=4}

model_Check(FullModel)



```


Graphs
====================


By AIC with linear model superimposed
--------------------
 

```{r, fig.height=7, fig.width=13}


cat("Model:", as.character(FullModel@call[2]), sep = '\n')

InstarGridGraph(dataset, "condResiduals", "Condition", "n", "", FullModel, "y")



```

Instar Age x nest size Interaction Graph
--------------------
 

```{r, fig.height=7, fig.width=13}

#newMod <- update(FullModel,  . ~ . - logCtFm)
cat("Model:", as.character(FullModel@call[2]), sep = '\n')

a_predictDF <- expand.grid(logCtFm = seq(min(dataset$logCtFm), max(dataset$logCtFm), by = 0.1), 
		InstarNumber = c(4, 5, 6, 7), InstarSex = c("M", "F"), NestID = c("44.4EX12"))


a_predictDF$lmrPrd <- predict(FullModel, a_predictDF)

ggplot(data = a_predictDF, aes(x = logCtFm, y = lmrPrd, colour = as.factor(InstarNumber))) + geom_line(size = 1) + mytheme +
		ylab("Predicted Condition") + xlab("Log Count Females") + scale_colour_discrete(name = "Instar Age")


```

\pagebreak


Statistics using model with lowest AIC
====================


```{r Stats,  results='asis', echo = FALSE, comment = "", }

########### Continune from here!


TestInteraction  <- c("Testing Interaction Term nest size * instar", lmer(condResiduals ~ logCtFm +  (1|NestID), data = dataset, REML = FALSE))
TestNestSize <- c("Testing Nest Size plus nest size interactions", lmer(condResiduals ~  (1|NestID) , data = dataset, REML = FALSE))


RedModels <- list(TestInteraction, TestNestSize)

MRAnovaFun(FullModel, RedModels)

```

Testing individual instar numbers
--------------------

```{r IndInstars,  results='asis', echo = FALSE, comment = "", tab.cap = NULL, message = FALSE, warning = FALSE, hold = TRUE}


LMERS_fun <- function(dataset) { # function to test individual instars 	
    lmFull <- lmer(condResiduals ~  logCtFm + (1|NestID), data = dataset)
    lmRed <- lmer(condResiduals ~ (1|NestID), data = dataset)
    return(list(lmFull, lmRed))
	
    }


instarLMER <- dlply(dataset, .(InstarNumber),        
		function(x) LMERS_fun(x))


results <- lapply(instarLMER, FUN = function(x) anova(x[[1]], x[[2]], refit
= TRUE))

sig <- lapply(results, FUN = function(x) ifelse(x[,8][2] <= 0.05, " * SIGNIFICANT *", "not significant"))

cat("note: pops up saying 'refitting model(s) with ML (instead of REML)'", "but if make anova refit = FALSE results don't make sense", sep = '\n')

kable(results$'7', caption = paste("Adult - age 7", sig$'7'))

kable(results$'6', caption = paste("Sub2 and Adult Males - age 6", sig$'6'))

kable(results$'5', caption = paste("Sub1 and sub males- age 5", sig$'5'))

kable(results$'4', caption = paste("Juv4 - age 4", sig$'4'))

	
```

Graph of condition variance against instar
====================

```{r, fig.height=6, fig.width=8, echo = FALSE}
ggplot(data = dataset, aes(x = as.factor(InstarNumber), y = condResiduals, fill = InstarSex)) +
	labs(x = "Instar") + labs(y = "Condition") + geom_boxplot() + mytheme
