
---
title: "Weight Vs Nest Size Results"
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE)
	
```

Leg Vs. Nest Size
--------------------

```{r LegNS, results='asis',  echo = FALSE}
##### Leg length vs nest size


FullModel <- lmer(logLeg ~  logCtFm + Instar + logCtFm:Instar  +  (1|NestID)  , data = spidersMul, REML = FALSE)
NSModel <- lmer(logLeg ~  Instar + (1|NestID)  , data = spidersMul, REML = FALSE)

NSResults <- outputResultsWord(FullModel, NSModel)
	
```

Leg length increases as nest size increases (lmer; $\chi$^2^~`r NSResults[[1]]`
,`r NSResults[[2]]`~= `r NSResults[[3]]`, p = `r NSResults[[4]]`
`r NSResults[[5]]`).


```{r LegInstar, results='asis',  echo = FALSE}
##### Leg length vs instar
FullModel <- lmer(logLeg ~  logCtFm + Instar + logCtFm:Instar  +  (1|NestID)  , data = spidersMul, REML = FALSE)
InstarModel <- lmer(logLeg ~  logCtFm + (1|NestID)  , data = spidersMul, REML = FALSE)

InstarResults <- outputResultsWord(FullModel, InstarModel)
	
```
Leg length is significantly correlated with instar, but that is not surprising (lmer; $\chi$^2^~`r InstarResults[[1]]`
,`r InstarResults[[2]]`~= `r InstarResults[[3]]`, p = `r InstarResults[[4]]`
`r InstarResults[[5]]`).

```{r LegInteraction, results='asis',  echo = FALSE}
##### Leg length vs instar
FullModel <- lmer(logLeg ~  logCtFm + Instar + logCtFm:Instar  +  (1|NestID)  , data = spidersMul, REML = FALSE)
InstarModel <- lmer(logLeg ~  logCtFm + Instar +  (1|NestID)  , data = spidersMul, REML = FALSE)

Results <- outputResultsWord(FullModel, InstarModel)
	
```
There is a significant interaction between instar and nest size (lmer; $\chi$^2^~`r Results[[1]]`,`r Results[[2]]`~ =
`r Results[[3]]`, p = `r Results[[4]]` `r Results[[5]]`).



```{r LegIndInstar, results='asis',  echo = FALSE}
##### Leg length vs interaction

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))

AdultRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Sub2"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Sub2"))

Sub2Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Sub1"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Sub1"))

Sub1Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Juv4"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Juv4"))

Juv4Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))

AdMaleRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))

SubMaleRes <- outputResultsWord(FullModel, RedModel)
	
```

Testing each instar separately, the only juvenile stage 4 and subadult stage 1
spiders did not show a significant decrease in leg length with nest size (table
1). 

| Instar   |      $\chi$^2^        |  p value                                | 
|----------|---------------------|--------------------------------------| 
|Adult  |  `r (AdultRes[[3]])` |`r AdultRes[[4]]` `r AdultRes[[5]]`  | 
| Sub2 | `r (Sub2Res[[3]])` |   `r Sub2Res[[4]]` `r Sub2Res[[5]]`  | 
| Sub1 | `r (Sub1Res[[3]])` |   `r Sub1Res[[4]]` `r Sub1Res[[5]]`  | 
|Juv4 | `r (Juv4Res[[3]])` |   `r Juv4Res[[4]]` `r Juv4Res[[5]]`  | 
|Adult Male | `r (AdMaleRes[[3]])` |   `r AdMaleRes[[4]]` `r AdMaleRes[[5]]`  | 
|Sub Male| `r (SubMaleRes[[3]])` |   `r SubMaleRes[[4]]` `r SubMaleRes[[5]]`  | 

Table 1: Statistical results of leg length against nest size for each
instar tested individually

```{r LegGraph, fig.height=7, fig.width=13}

FullModel <- lmer(logLeg ~  logCtFm + Instar + logCtFm:Instar  + 
				(1|NestID)  , data = spidersMul, REML = FALSE)



InstarGridGraph(spidersMul, "logLeg", "Leg Length - log transformed", "n", "", FullModel)

```
  
Figure 1: Leg length against nest size. The overlaid model
is `r as.character(FullModel@call[2])`. Overall leg length decreases with
nest size (p = `r NSResults[[4]]` `r NSResults[[5]]`) and there is a
significant interaction with instar(p = `r InstarResults[[4]]`
`r InstarResults[[5]]`).


Condition Vs. Nest Size
--------------------



```{r CondNS, results='asis',  echo = FALSE}
##### Leg length vs nest size


FullModel <- lmer(condResiduals ~  logCtFm + Instar + logCtFm:Instar  +  (1|NestID)  , data = spidersMul, REML = FALSE)
NSModel <- lmer(condResiduals ~  Instar + (1|NestID)  , data = spidersMul, REML = FALSE)

NSResults <- outputResultsWord(FullModel, NSModel)
	
```

Condition decreases as nest size increases (lmer; $\chi$^2^~`r NSResults[[1]]`
,`r NSResults[[2]]`~= `r NSResults[[3]]`, p = `r NSResults[[4]]`
`r NSResults[[5]]`).


```{r ConditionInstar, results='asis',  echo = FALSE}
##### Leg length vs instar
FullModel <- lmer(condResiduals ~  logCtFm + Instar + logCtFm:Instar  +  (1|NestID)  , data = spidersMul, REML = FALSE)
InstarModel <- lmer(condResiduals ~  logCtFm + (1|NestID)  , data = spidersMul, REML = FALSE)

InstarResults <- outputResultsWord(FullModel, InstarModel)
	
```
Condition is significantly correlated with instar (lmer; $\chi$^2^~`r InstarResults[[1]]`
,`r InstarResults[[2]]`~= `r InstarResults[[3]]`, p = `r InstarResults[[4]]`
`r InstarResults[[5]]`).

```{r ConditionInteraction, results='asis',  echo = FALSE}
##### Leg length vs instar
FullModel <- lmer(condResiduals ~  logCtFm + Instar + logCtFm:Instar  +  (1|NestID)  , data = spidersMul, REML = FALSE)
InstarModel <- lmer(condResiduals ~  logCtFm + Instar +  (1|NestID)  , data = spidersMul, REML = FALSE)

Results <- outputResultsWord(FullModel, InstarModel)

FullModel <- lmer(condResiduals ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
RedModel <- lmer(condResiduals ~  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
AdultResults <- outputResultsWord(FullModel, RedModel)
		
	
```
Again there is a significant interaction between instar and nest size (lmer; $\chi$^2^~`r Results[[1]]`,`r Results[[2]]`~ =
`r Results[[3]]`, p = `r Results[[4]]` `r Results[[5]]`). When performing ad-hoc tests on the instars individually we find that only adult 
condition decreases with nest size (lmer; $\chi$^2^~`r AdultResults[[1]]`,`r AdultResults[[2]]`~ =
`r AdultResults[[3]]`, p = `r AdultResults[[4]]` `r AdultResults[[5]]`).


```{r ConditionGraph, fig.height=7, fig.width=13}

FullModel <- lmer(condResiduals ~  logCtFm + Instar + logCtFm:Instar  + 
				(1|NestID)  , data = spidersMul, REML = FALSE)



InstarGridGraph(spidersMul, "condResiduals", "Individual Condition", "n", "", FullModel)

```
  
Figure
2: Individual condition against nest size. The overlaid model is
`r as.character(FullModel@call[2])`. Overall leg length decreases with nest size
(p = `r NSResults[[4]]` `r NSResults[[5]]`) and there is a significant
interaction with instar(p = `r InstarResults[[4]]` `r InstarResults[[5]]`).


Original Nest Vs Propagule
--------------------

```{r LegSing, results='asis',  echo = FALSE}
##### Leg length vs nest size


FullModel <- lmer(logLeg ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSModel <- lmer(logLeg ~   (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)

NSResults <- outputResultsWord(FullModel, NSModel)
	
```
  
Leg length is larger in propagules compared to the source nest (lmer;
$\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~= `r NSResults[[3]]`, p =
`r NSResults[[4]]` `r NSResults[[5]]`).



```{r CondSing, results='asis',  echo = FALSE}
##### Leg length vs nest size


FullModel <- lmer(condResiduals ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSModel <- lmer(condResiduals ~  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)

NSResults <- outputResultsWord(FullModel, NSModel)
	
```

Individuals in propagules have greater conditions compared to those in the
original nests (lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~=
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`).

```{r SingGraphs, fig.height=9, fig.width=13}

p1 <- ggplot(nestsToTestSigCond, aes(x=type, y=condResiduals)) + geom_boxplot() + 
		ylab("Individual Condition") + mytheme+ theme(axis.title.x = element_blank()) +
		scale_x_discrete(breaks=c("multiple", "single"), labels=c("source: multiple", "propagules: single"))

p2 <- ggplot(nestsToTestSig, aes(x=type, y=logLeg)) + geom_boxplot()  +
		mytheme +  theme(axis.title.x = element_blank()) +
		scale_x_discrete(breaks=c("multiple", "single"), labels=c("source: multiple", "propagules: single"))


grid.arrange(p1, p2, ncol = 2)


```
  
Figure 3: Condition and leg length of adult females in propagues and their source nest