
---
title: "Weight Vs Colony Size Results with instar as numeric"
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE)
	
```

Leg Vs. Colony Size
--------------------

```{r LegNS, results='asis',  echo = FALSE}
##### Leg length vs colony size

FullModel <- lmer(logLeg ~ logCtFm + logCtFm:InstarNumber:InstarSex + logCtFm:InstarNumber + 
    			InstarSex:InstarNumber + InstarNumber + InstarSex + (1|NestID), data = spidersMul, REML = FALSE)

NSModel <- lmer(logLeg ~ InstarSex:InstarNumber + InstarNumber + InstarSex + (1|NestID)  , data = spidersMul, REML = FALSE)

NSResults <- outputResultsWord(FullModel, NSModel)
	
```

The model with the lowest AIC was (`r as.character(FullModel@call[2])`). Using this as the full model we found that
leg length increases as colony size increases (lmer; $\chi$^2^~`r NSResults[[1]]`
,`r NSResults[[2]]`~= `r NSResults[[3]]`, p = `r NSResults[[4]]`
`r NSResults[[5]]`).


```{r LegInstarNumber, results='asis',  echo = FALSE}
##### Leg length vs instar

InstarModel <- lmer(logLeg ~ logCtFm  + InstarSex + (1|NestID) , data = spidersMul, REML = FALSE)

InstarResults <- outputResultsWord(FullModel, InstarModel)
	
```

Leg length was significantly correlated with instar age, but that is not surprising due to their different physiology (lmer; $\chi$^2^~`r InstarResults[[1]]`
,`r InstarResults[[2]]`~= `r InstarResults[[3]]`, p = `r InstarResults[[4]]`
`r InstarResults[[5]]`).


```{r LegInstarSex, results='asis',  echo = FALSE}
##### Leg length vs instar

InstarSexModel <- lmer(logLeg ~ logCtFm  + logCtFm:InstarNumber + InstarNumber + (1|NestID), data = spidersMul, REML = FALSE)

InstarSexResults <- outputResultsWord(FullModel, InstarModel)
	
```

In addition, leg length was significantly correlated with instar sex, but (lmer; $\chi$^2^~`r InstarSexResults[[1]]`
,`r InstarSexResults[[2]]`~= `r InstarSexResults[[3]]`, p = `r InstarSexResults[[4]]`
`r InstarSexResults[[5]]`).

```{r LegThreeWayInteraction, results='asis',  echo = FALSE}
##### Leg length vs instar
ThreeIntModel <- lmer(logLeg ~ logCtFm  + logCtFm:InstarNumber + 
    			InstarSex:InstarNumber + InstarNumber + InstarSex +  (1|NestID)  , data = spidersMul, REML = FALSE)

Results <- outputResultsWord(FullModel, ThreeIntModel)
	
```
The three way interaction was not significant (lmer; $\chi$^2^~`r Results[[1]]`,`r Results[[2]]`~ =
`r Results[[3]]`, p = `r Results[[4]]` `r Results[[5]]`). 


```{r LegNSInstarNumInt, results='asis',  echo = FALSE}
##### Leg length vs instar
NSInsIntModel <- lmer(logLeg ~ logCtFm + InstarSex +  (1|NestID)  , data = spidersMul, REML = FALSE)

Results <- outputResultsWord(FullModel, NSInsIntModel)
	
```
However the instar age x nest size interaction was significant (lmer; $\chi$^2^~`r Results[[1]]`,`r Results[[2]]`~ =
`r Results[[3]]`, p = `r Results[[4]]` `r Results[[5]]`). 

As the effect of colony size on spider size was absent in the youngest instars (Table 1); it was first detectable in subadult males and females.



```{r LegIndInstar, results='asis',  echo = FALSE}
##### Leg length vs interaction

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))

AdultRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Sub2"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Sub2"))

Sub2Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Sub1"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Sub1"))

Sub1Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Juv4"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "Juv4"))

Juv4Res <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "AdMale"))

AdMaleRes <- outputResultsWord(FullModel, RedModel)

FullModel <- lmer(logLeg ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))
RedModel <- lmer(logLeg ~  (1|NestID)  , data = subset(spidersMul, Instar == "SubMale"))

SubMaleRes <- outputResultsWord(FullModel, RedModel)
	
```

Testing each instar separately, the only juvenile stage 4 and subadult stage 1
spiders did not show a significant decrease in leg length with colony size (table
1). 

| Instar   |      $\chi$^2^        |  p value                                | 
|----------|---------------------|--------------------------------------| 
|Juv4 | `r (Juv4Res[[3]])` |   `r Juv4Res[[4]]` `r Juv4Res[[5]]`  | 
| Sub1 | `r (Sub1Res[[3]])` |   `r Sub1Res[[4]]` `r Sub1Res[[5]]`  | 
| Sub2 | `r (Sub2Res[[3]])` |   `r Sub2Res[[4]]` `r Sub2Res[[5]]`  | 
|Adult  |  `r (AdultRes[[3]])` |`r AdultRes[[4]]` `r AdultRes[[5]]`  |  
|Sub Male| `r (SubMaleRes[[3]])` |   `r SubMaleRes[[4]]` `r SubMaleRes[[5]]`  | 
|Adult Male | `r (AdMaleRes[[3]])` |   `r AdMaleRes[[4]]` `r AdMaleRes[[5]]`  | 


Table 1: Statistical results of leg length against colony size for each
instar tested individually

```{r LegGraph, fig.height=7, fig.width=13}

FullModel <- lmer(logLeg ~  logCtFm + Instar + logCtFm:Instar  + 
				(1|NestID)  , data = spidersMul, REML = FALSE)



InstarGridGraph(spidersMul, "logLeg", "Leg Length - log transformed", "n", "", FullModel)

```
  
(@) Figure:  Leg length against colony size. The overlaid model
is `r as.character(FullModel@call[2])`. Overall leg length decreases with
colony size (p = `r NSResults[[4]]` `r NSResults[[5]]`) and there was a
significant interaction with instar (p = `r InstarResults[[4]]`
`r InstarResults[[5]]`).


Condition Vs. Colony Size
--------------------



```{r CondNS, results='asis',  echo = FALSE}
##### Leg length vs colony size


FullModel <- lmer(condResiduals ~  logCtFm + Instar + logCtFm:Instar  +  (1|NestID)  , data = spidersMul, REML = FALSE)
NSModel <- lmer(condResiduals ~  Instar + (1|NestID)  , data = spidersMul, REML = FALSE)

NSResults <- outputResultsWord(FullModel, NSModel)
	
```
Again the model with the lowest AIC included colony size, instar and instar x colony size interaction.
Condition decreases as colony size increases (lmer; $\chi$^2^~`r NSResults[[1]]`
,`r NSResults[[2]]`~= `r NSResults[[3]]`, p = `r NSResults[[4]]`
`r NSResults[[5]]`).


```{r ConditionInstar, results='asis',  echo = FALSE}
##### Leg length vs instar
FullModel <- lmer(condResiduals ~  logCtFm + Instar + logCtFm:Instar  +  (1|NestID)  , data = spidersMul, REML = FALSE)
InstarModel <- lmer(condResiduals ~  logCtFm + (1|NestID)  , data = spidersMul, REML = FALSE)

InstarResults <- outputResultsWord(FullModel, InstarModel)
	
```
Condition was significantly correlated with instar (lmer; $\chi$^2^~`r InstarResults[[1]]`
,`r InstarResults[[2]]`~= `r InstarResults[[3]]`, p = `r InstarResults[[4]]`
`r InstarResults[[5]]`).

```{r ConditionInteraction, results='asis',  echo = FALSE}
##### Leg length vs instar
FullModel <- lmer(condResiduals ~  logCtFm + Instar + logCtFm:Instar  +  (1|NestID)  , data = spidersMul, REML = FALSE)
InstarModel <- lmer(condResiduals ~  logCtFm + Instar +  (1|NestID)  , data = spidersMul, REML = FALSE)

Results <- outputResultsWord(FullModel, InstarModel)

FullModel <- lmer(condResiduals ~  logCtFm +  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
RedModel <- lmer(condResiduals ~  (1|NestID)  , data = subset(spidersMul, Instar == "Adult"))
AdultResults <- outputResultsWord(FullModel, RedModel)
		
	
```
Again there was a significant interaction between instar and colony size (lmer; $\chi$^2^~`r Results[[1]]`,`r Results[[2]]`~ =
`r Results[[3]]`, p = `r Results[[4]]` `r Results[[5]]`). When performing ad-hoc tests on the instars individually we find that only adult 
condition decreases with colony size (lmer; $\chi$^2^~`r AdultResults[[1]]`,`r AdultResults[[2]]`~ =
`r AdultResults[[3]]`, p = `r AdultResults[[4]]` `r AdultResults[[5]]`).


```{r ConditionGraph, fig.height=7, fig.width=13}

FullModel <- lmer(condResiduals ~  logCtFm + Instar + logCtFm:Instar  + 
				(1|NestID)  , data = spidersMul, REML = FALSE)



InstarGridGraph(spidersMul, "condResiduals", "Individual Condition", "n", "", FullModel, "y")

```
  
(@)  Figure : Individual condition against colony size. The overlaid model is
`r as.character(FullModel@call[2])`. Overall leg length decreases with colony size
(p = `r NSResults[[4]]` `r NSResults[[5]]`) and there was a significant
interaction with instar(p = `r InstarResults[[4]]` `r InstarResults[[5]]`).



Within Colony Variance Vs. colony size
--------------------

### Condition Variance

```{r CondVar, results='asis',  echo = FALSE}

FullModel <- lmer(relativeVar ~  logCtFm + Instar +  (1|NestID)  , data = condVar, REML = FALSE)
Model <- lmer(relativeVar ~  logCtFm + (1|NestID)  , data = condVar, REML = FALSE)

IntResults <- outputResultsWord(FullModel, Model)

Model <- lmer(relativeVar ~  Instar + (1|NestID)  , data = condVar, REML = FALSE)

NSResults <- outputResultsWord(FullModel, Model)
	
```

The model with the lowest AIC value only included colony size and instar as explanatory factors.
Instar was significant (lmer; $\chi$^2^~`r Results[[1]]`
,`r IntResults[[2]]`~= `r IntResults[[3]]`, p = `r IntResults[[4]]`
`r IntResults[[5]]`), however colony size was not (lmer; $\chi$^2^~`r NSResults[[1]]`
,`r NSResults[[2]]`~= `r NSResults[[3]]`, p = `r NSResults[[4]]`
`r NSResults[[5]]`).


```{r ConditionVarGraph, fig.height=7, fig.width=13}


InstarGridGraph(condVar, "relativeVar", "Variance in Condition", "n", "", FullModel, "y")

```
  
(@)  Figure : Variance in condition against colony size


```{r instarCondVarGraph, fig.height=4, fig.width=7, echo = FALSE}
ggplot(data = condVar, aes(x = Instar, y = relativeVar, fill = InstarSex)) +
	labs(x = "Instar") + labs(y = "Variance in Condition") + geom_boxplot() + mytheme

```
   
(@) Figure :Condition variance within colonies by instar. I am not sure yet whether
this is a real results and/or intereseting to the story




### Leg Length Variance


```{r LegLenVar, results='asis',  echo = FALSE}
##### Leg length vs colony size


FullModel <- lmer(relativeVar ~  logCtFm + Instar +  (1|NestID)  , data = legVar, REML = FALSE)
Model <- lmer(relativeVar ~  logCtFm + (1|NestID)  , data = legVar, REML = FALSE)

IntResults <- outputResultsWord(FullModel, Model)

Model <- lmer(relativeVar ~  Instar + (1|NestID)  , data = legVar, REML = FALSE)

NSResults <- outputResultsWord(FullModel, Model)
	
```


The model with the lowest AIC value only included colony size and instar as explantory factors.
Instar was not significant (lmer; $\chi$^2^~`r Results[[1]]`
,`r IntResults[[2]]`~= `r IntResults[[3]]`, p = `r IntResults[[4]]`
`r IntResults[[5]]`), neither was colony size (lmer; $\chi$^2^~`r NSResults[[1]]`
,`r NSResults[[2]]`~= `r NSResults[[3]]`, p = `r NSResults[[4]]`
`r NSResults[[5]]`).


```{r instarLegVarGraph, fig.height=4, fig.width=7, echo = FALSE}
ggplot(data = legVar, aes(x = Instar, y = relativeVar, fill = InstarSex)) +
	labs(x = "Instar") + labs(y = "Variance in Leg Length") + geom_boxplot() + mytheme

```
   
(@) Figure :Leg length variance within colonies by instar. I am not sure yet whether
this is a real results and/or intereseting to the story



Original Colony Vs Propagule
--------------------

```{r LegSing, results='asis',  echo = FALSE}
##### Leg length vs colony size


FullModel <- lmer(logLeg ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSModel <- lmer(logLeg ~   (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)

NSResults <- outputResultsWord(FullModel, NSModel)
	
```
  
Leg length was larger in propagules compared to the source colony (lmer;
$\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~= `r NSResults[[3]]`, p =
`r NSResults[[4]]` `r NSResults[[5]]`).



```{r CondSing, results='asis',  echo = FALSE}
##### Leg length vs colony size


FullModel <- lmer(condResiduals ~  type  +  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)
NSModel <- lmer(condResiduals ~  (1|NestID) + (1|OrigNest) , data = nestsToTestSig, REML = FALSE)

NSResults <- outputResultsWord(FullModel, NSModel)
	
```

Individuals in propagules have better condition compared to those in the
original nests (lmer; $\chi$^2^~`r NSResults[[1]]`,`r NSResults[[2]]`~=
`r NSResults[[3]]`, p = `r NSResults[[4]]` `r NSResults[[5]]`).

```{r SingGraphs, fig.height=6, fig.width=12}

p1 <- ggplot(nestsToTestSigCond, aes(x=type, y=condResiduals)) + geom_boxplot() + 
		ylab("Individual Condition") + mytheme+ theme(axis.title.x = element_blank()) +
		scale_x_discrete(breaks=c("multiple", "single"), labels=c("source: multiple", "propagules: single"))

p2 <- ggplot(nestsToTestSig, aes(x=type, y=logLeg)) + geom_boxplot()  +
		mytheme +  theme(axis.title.x = element_blank()) +
		scale_x_discrete(breaks=c("multiple", "single"), labels=c("source: multiple", "propagules: single"))


grid.arrange(p1, p2, ncol = 2)


```
  
(@) Figure: Condition and leg length of adult females in propagues and their
source nest


Propagule survival
--------------------

We found that nests with single females spiders had a very low survival rate
(figure 5).

```{r PropaguleSurvivalGraph, fig.height=4, fig.width=4}

ggsurvplot(prop.survfit,color = "#2E9FDF", break.time.by = 5, 
		xlab = "Days until propagule death", ylab = "Propagule survival probability",  censor = FALSE)

nProps <- nlevels(props$propID)
nOriginalNests <- nlevels(props$nestID)

```
  
(@) Figure:  The survival function of `r nProps` propagules from `r nOriginalNests`
source nests.