

---
title: "Leg Length vs Nest Size with sex and instar as numeric"
output:
  pdf_document:
    toc: true
author: "Ruth Sharpe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: margin=1.5cm
header-includes:
    - \usepackage{caption}
---

\captionsetup[table]{labelformat=empty}

```{r docOptions, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, error = FALSE)
	
```


AIC Values of all possible models with instar always included
====================

```{r AIC, results='asis',  echo = FALSE}
#pander options http://rapporter.github.io/pander/#general-options

outcome    <- c("logLeg")
predictors <- c("logCtFm", "logCtFm:InstarNumber:InstarSex", "logCtFm:InstarNumber", "InstarSex:InstarNumber", "InstarSex:logCtFm")
dataset    <- spidersMul

modTable <- allModelsAICWithSex(outcome, predictors, dataset)
lowestAICMod <- as.character(modTable$model[1])

formula    <- as.formula(lowestAICMod)
FullModel       <- lmer(formula, data = dataset, REML = FALSE)


row.names(modTable) <- NULL # removing row names

panderOptions('table.split.table', Inf)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('keep.line.breaks', TRUE)


pander(modTable,  row.names = NULL, justify = 'left', split.cells = c(1, 2, 61, 2))
	
```



Graph with lowest AIC model superimposed
====================
 

```{r Graph, fig.height=7, fig.width=13}


cat("Model:", as.character(FullModel@call[2]), sep = '\n')

InstarGridGraph(dataset, "logLeg", "Leg Length - log transformed", "n", "", FullModel)

```

\pagebreak


Statistics
====================
Note: There is no point testing instar number against leg length as it will vary of course, same with instar size


```{r Stats,  results='asis', echo = FALSE, comment = "", message = FALSE}



Test3WayInteraction <- c("Three way interaction", lmer(logLeg ~ logCtFm + logCtFm:InstarNumber + InstarSex:InstarNumber + InstarNumber + InstarSex +  (1|NestID)   + (1|NestID)  , data = dataset, REML = FALSE))
TestInteraction2 <- c("Nest size x Instar Number", lmer(logLeg ~ logCtFm  + logCtFm:InstarNumber + InstarNumber + InstarSex +  (1|NestID), data = dataset, REML = FALSE))
TestSex <- c("Spider Sex", lmer(logLeg ~ logCtFm + logCtFm:InstarNumber + InstarNumber  +  (1|NestID), data = dataset, REML = FALSE))
TestNS <- c("NestSize", lmer(logLeg ~ InstarSex:InstarNumber + InstarNumber + InstarSex +  (1|NestID)  , data = dataset, REML = FALSE))

RedModels <- list(Test3WayInteraction, TestInteraction2, TestSex, TestNS)

MRAnovaFun(FullModel, RedModels)

```
\pagebreak

Testing Individual Instars
====================
###As the interaction is significant testing instar individually



```{r IndInstars,  results='asis', echo = FALSE, comment = "", tab.cap = NULL, message = FALSE, warning = FALSE, hold = TRUE}


LMERS_fun <- function(myData) { # function to test individual instars 	
    lmFull <- lmer(logLeg ~  logCtFm + (1|NestID), data = myData)
    lmRed <- lmer(logLeg ~  + (1|NestID), data = myData)
    return(list(lmFull, lmRed))
	
    }


instarLMER <- dlply(dataset, .(Instar),        
		function(x) LMERS_fun(x))


results <- lapply(instarLMER, FUN = function(x) anova(x[[1]], x[[2]], refit
= TRUE))

cat("note: pops up saying 'refitting model(s) with ML (instead of REML)'", "but if make anova refit = FALSE results don't make sense", sep = '\n')

kable(results$Adult, caption = "Adult")

kable(results$Sub2, caption = "Sub2")

kable(results$Sub1, caption = "Sub1")

kable(results$Juv4, caption = "Juv4")

```

\pagebreak


```{r IndInstars2,  results='asis', echo = FALSE, comment = "", tab.cap = NULL, message = FALSE, warning = FALSE, hold = TRUE}

kable(results$AdMale, caption = "AdMale")

kable(results$SubMale, caption = "SubMale")
	
```







